\newenvironment{acknowledgements}%
    {\cleardoublepage\thispagestyle{empty}\null\vfill\begin{center}%
    \bfseries Acknowledgements\end{center}}%
    {\vfill\null}
        \begin{acknowledgements}
        
        First and foremost, I want to express my deep gratitude to my advisor Kathryn Hess for taking me as her PhD student, sharing her knowledge and insights, and providing an excellent research environment.
        This thesis would not exist without her constant support, encouragement and availability, and giving me the freedom of developing my own research interest.
        I also want to thank Gijs Heuts for acting as an unofficial co-supervisor, answering my questions and sharing his profound knowledge in homotopy theory.
        It is a great honor for me to work with him.
        
        Moreover, I'm grateful Hadrian Heine for explaining the results in his PhD thesis and many enlightening suggestions in this thesis. I also want to thank Markus Hausmann, Ben Knudsen, Lennart Meier and Jerome Scherer who had shared their knowledge and insights in homotopy theory with me.
        
        I want to thank all my academic siblings at EPFL, Adelie, Aras, Celia, Kelly, Lavenir, Lyne, Olivia, Samuel and Stefania for the joy and mathematical discussions along this journey.
        % Also, I appreciate the math discussions and countless lunches I had with the members at the UPHESS group; Anibal, Nicolas Berkouk, 
        % Daniela Santander, Jens Kjaer, Inbar Klang, Darrick Lee, Anibal Medina-Mardones, Nicolas Ninin, Raphael Reinauer, Nima Rasekh, Beren Sanders, Martina Scolamiero, Kürşat Sözer, Gard Spreemann and Guillaume Tauzin. 
        I want to thank our secretary Maroussia Schaffner for her hard work and support from the administrative side of my time at EPFL.
        
        I want to thank the Chinese homotopy theory community for the invitation to the conferences in Shenzhen and Shanghai; special thanks go to Hana Jia Kong,
        Danny Xiaolin Shi, Guozhen Wang, Zhouli Xu, Yifei Zhu. 
        I will miss the online Higer Topos Theory and Higher Algebra seminar during the COVID time with my fellow colleagues, Guchuan Li, Yunze Lu, Yuqing Shi, Mingcong Zeng and Foling Zou.
        
        My westward journey to Switzerland wouldn't be so colorful without the accompany of my close friends. I'm indebted to my friends I knew from Zurich; Chong, Jiqing, Junliang and Yukun had enlightened me on how to learn and do research in pure math;
        Hanlin, Qian and Yuhang had revived my interest of doing research in the financial market;
        Leandra for our friendship throughout the last 8 years in China and Switzerland.
        I also appreciate the accompany of my friends in Lausanne; especially to Hao, Shengquan, Weizhe and Zhiwen for all the joy and happiness we shared in the 3 common years we spent at EPFL.
        Special thanks go to Boris, Clara, Marika and Zheng for keeping my final year at EPFL not so lonely.
        
        Last but not the least, I want to thank my parents for all the support and understanding of my every decision.
        
        
        
        





        \end{acknowledgements}
        