\chapter{Koszul Duality}

In this chapter, we provide the necessary background on $\infty$-operads (resp. $\infty$-cooperads) and algebras (resp. coalgebras) over them. For convenience, we will assume $\CC$ is a pointed, presentably symmetric monoidal $\infty$-category throughout this chapter.

Our main references will be \cite{BrantnerPhD},  \cite{Heuts_Koszul}, \cite{Francis-Gaitsgory}, \cite{Hadrianphdthesis} and \cite{HA}.
 
In \S \ref{(co)Operads in Infinity-Categories}, we define $\infty$-operads and $\infty$-cooperads in a symmetric monoidal $\infty$-category $\CC$, as associative algebras and associative coalgebras in the $\infty$-category of symmetric sequences in $\CC$, respectively.

In \S \ref{Algebras over Operads}, we discuss algebras over an $\infty$-operad and some relevant constructions which will be useful in the proof of the main theorems. 

In \S \ref{Coalgebras over cooperads and Koszul Duality}, we explain the bar-cobar duality between connected $\infty$-operads and cooperads. We then define divided power, conilpotent coalgebras over a $\infty$-cooperad and define the Koszul duality functor $\indec_{\CO}$.

In \S \ref{The spectral Lie operad}, we define the spectral Lie operad and introduce shifting of an $\infty$-operad and relevant properties.

In \S \ref{Section: Induced Monads}, we explain how to produce monads and comonads on $\Sp^{\geq r}$ and $\Sp^{\geq r}_{\tame}$ from certain monads and comonads on $\Sp$.

In \S \ref{Commutative coalgebras in tame spectra}, we define the $\infty$-category of commutative coalgebras in an $\infty$-category. In the case of tame spectra, we prove that it is equivalent to the $\infty$-category of divided power, conilpotent coalgebras.

In \S \ref{Lie Algebras in Tame Spectra}, we define spectral Lie algebras and tame spectral Lie algebras. We then use Koszul duality between the spectral Lie operad and commutative operad to define the Chevalley-Eilenberg functor as a functor from the $\infty$-category of tame spectral Lie algebras to the $\infty$-category of divided power, conilpotent commuative coalgebras in tame spectra.




\section{(co)Operads in Infinity-Categories}
\label{(co)Operads in Infinity-Categories}
In this section, we collect and extend some results from \cite{BrantnerPhD} and \cite{Hadrianphdthesis}.

Let $\Fin^{\simeq}$ denote the $\infty$-category of finite sets with bijections between them, i.e., the core of $\Fin$. 
Note that $\Fin^{\simeq}$ carries a natural symmetric monoidal structure with the tensor product given by the disjoint union. 
Moreover, it's the free symmetric monoidal $\infty$-category generated by the one-object category $\{*\}$.
The $\infty$-category $\CP(\Fin^{\simeq})$ of presheaves admits a symmetric monoidal structure given by Day convolution \cite[Example 2.2.6.9.]{HA}, hence we can also consider it as a presentable symmetric monoidal $\infty$-category. This suggests an alternative description of $\CC$:
\[
\Fun_{\CAlg(\Pr^L)}(\CP(\Fin^{\simeq}), \CC) 
\simeq 
\Fun_{\CAlg(\Cat_{\infty})} (\Fin^{\simeq}, \CC)
\simeq
\Fun(\{*\}, \CC)
\simeq 
\CC.
\]


\begin{definition}
	A \emph{symmetric sequence} in $\CC$ is a functor 
	$$
	A:\Fin^{\simeq} \to \CC.
	$$ We denote the $\infty$-category of symmetric sequences in $\CC$ by $\SSeq(\CC)$.
\end{definition}
\begin{remark}
	Informally, one can think of a symmetric sequence $A$ in $\CC$ as a sequence of objects $\{A(n)\}_{n\geq 0}$ in $\CC$ where $A(n):= A((n))$ carries an action of $\Sigma_n$ for each $n$.
	We will refer to the number $n$ as the \emph{arity} of the symmetric sequence $A$. We will sometimes describe an $\infty$-operad informally by giving a sequence $\{A(0), A(1), \dots \}$.
	
\end{remark}
Recall the $\infty$-category of presentable $\infty$-categories admits a symmetric monoidal structure. The tensor product $\otimes$ in $\Pr^L$ admits an explicit formula as in \cite[Proposition 4.8.1.17.]{HA}. The following lemma points out that the $\infty$-category $\SSeq(\CC)$ of symmetric sequences in $\CC$ is tensored over the $\infty$-category $\SSeq(\Space)$ of symmetric sequences in the $\infty$-category $\CS$ of spaces.
\begin{lemma}
	 Let $\CC$ be a presentably symmetric moniodal $\infty$-category.
	Then
	$$
	\SSeq(\CC) \simeq \SSeq(\Space)\otimes \CC
	\simeq \CP(\Fin^{\simeq})\otimes \CC.
	$$
\end{lemma}
\begin{proof}
First note that 
$
\SSeq(\Space)=\Fun(\Fin^{\simeq}, \Space)\simeq \CP(\Fin^{\simeq}),
$
since $\Fin^{\simeq}$ is isomorphic to its opposite category. This proves the second equivalence.
Using \cite[Proposition 4.8.1.17.]{HA}, we deduce that there are equivalences
\begin{align*}
	\SSeq(\Space)\otimes \CC 
& \simeq 
\Fun^R(\CP(\Fin^{\simeq})^{op},\CC)\\
&\simeq
(\Fun^{L}(\CP(\Fin^{\simeq}), \CC^{op}))^{op}\\
& \simeq
\Fun(\Fin^{\simeq},\CC^{op}) ^{op}\\
& \simeq \SSeq(\CC).
\end{align*}



\end{proof}

% The category of symmetric sequences $\SSeq(\CD)$ in $\CD$ has a monoidal product $\circ$ called the \emph{composition product}, defined so that the functor $\theta$ is a monoidal functor with respect to the composition monoidal structure in the codomain.   An \emph{ordinary operad} in $\CD$ is then defined as an associative monoid object with respect to this composition product.
%
%For our usage, we need a version of $\infty$-operads enriched in $\CC$. For this we need three ingredients, symmetric sequences, composition products and associative monoid objects. 
%The $\infty$-category $\SSeq(\CC)$ of \emph{symmetric sequences} in $\CC$ is defined as $\Fun(\Fin^{\simeq},\CC)$. 
%Given a symmetric sequence $\CO$ in $\SSeq(\CC)$, it has an associated monad on $\CC$ which is informally on an object $X\in \CC$ given by 
%$$
%\coprod_{n\geq 0} \CO(n)\otimes_{\Sigma_n} X^{\otimes n}.
%$$



We now explain a monoidal structure on $\SSeq(\CC)$ that will be used to define $\infty$-operads. Note that we can view $\CC$ as the full subcategory of $\SSeq(\CC)$ spanned by symmetric sequences that evaluates to the zero object on all non-empty finite sets in $\Fin^{\simeq}$. 
The $\infty$-category $\SSeq(\CC)$ of symmetric sequences is equipped with a monoidal structure that corresponds to the composition of functors in the $\infty$-category $\Fun_{\CAlg(\Pr^L)_{\CC/}}(\SSeq(\CC),\SSeq(\CC))$. More precisely, there are equivalences of $\infty$-categories

\begin{align*}
    	\Fun_{\CAlg(\Pr^L)_{\CC/}}(\SSeq(\CC),\SSeq(\CC))
	& \simeq 
\Fun_{\CAlg(\Pr^L)}(\CP(\Fin^{\simeq}),\SSeq(\CC))\\
& \simeq
\Fun_{\CAlg(\Cat_{\infty})}(\Fin^{\simeq},\SSeq(\CC))\\
& \simeq \Fun(\{*\}, \SSeq(\CC))\\
& \simeq \SSeq(\CC),
\end{align*}
allowing the transfer of the monoidal structure on $\Fun_{\CAlg(\Pr^L)_{\CC/}}(\SSeq(\CC),\SSeq(\CC))$ to $\SSeq(\CC)$.
Given two symmetric sequences $X$ and $Y$ in $\CC$, we will write $X\circ Y$ for this monoidal product on $\SSeq(\CC)$ and refer to it as the \emph{composition product}.


\begin{remark}
\label{formula for composition product}
For some categories $\CC$, e.g.,  $\CC=\operatorname{Set}, \Sp$ etc. with a point-set model, there is a concrete formula for the composition product (cf. \cite[Section 4.1.2.]{BrantnerPhD})
$$
A\circ B (J) \cong \coprod_{n\geq 0} \big(
\coprod_{J = J_1 \coprod \cdots \coprod J_n} A(\underline{n}) \otimes 
B(J_1)\otimes \cdots \otimes B(J_n)
\big)_{h\Sigma_n},
$$
where $\underline{n}$ denotes the finite set with $n$ elements and the second coproduct runs over all partitions of $J$. 
\end{remark}

\begin{remark}
\label{Schur functor}
Let $X \in \CC$ be an object in $\CC$, which we can identify as a symmetric sequence.
By the equivalence
$$
\Fun_{\CAlg(\Pr^L)_{\CC/}}(\SSeq(\CC),\SSeq(\CC))
\simeq
\SSeq(\CC),
$$
we can identify $X$ as a functor $\SSeq(\CC) \to \SSeq(\CC)$ that factors through $\CC$.
To any symmetric sequence $A$ in $\CC$,  we can then identify $A\circ X$ as an object $A(X)$ in $\CC$.
By Remark \ref{formula for composition product}, we obtain a functor which has an explicit description as follows
\begin{align*}
		F_{(-)}: \SSeq(\CC) & \rightarrow \Fun(\CC,\CC)\\
	A        & \mapsto \big( X\mapsto  A(X):=(\coprod_{n\geq 0} A(n)\otimes X^{\otimes n})_{h\Sigma_n}\big).
\end{align*}
where $\Sigma_n$ acts on the $n$-th tensor power of $X$ via permutation.
By our definition of the composition products, this assignment is monoidal with respect to the composition product in $\SSeq(\CC)$ (see \cite[\S 3.1 ]{Francis-Gaitsgory}) and composition of functors in $\Fun(\CC,\CC)$.
We call the the endofunctor $F_A$ the \emph{Schur functor associated to the symmetric sequence $A$}.
\end{remark}

We can now define $\infty$-operads (resp. $\infty$-cooperads) as associative algebras (resp. coalgebras) with respect to the composition products in $\SSeq{\CC}$.
\begin{definition}
	\label{inf operads}
	The \emph{$\infty$-category $\Opd(\CC)$ of $\infty$-operads in $\CC$} (resp. $\infty$-category $\Coop(\CC)$ of $\infty$-cooperads in $\CC$) is defined as the $\infty$-category $\Alg(\SSeq(\CC))$ (resp.$\coAlg(\SSeq(\CC))$) of associative algebras (resp. coalgebras) in $\SSeq(\CC)$ with respect to the composition product.
\end{definition}


\begin{remark}
Although Lurie's approach to $\infty$-operads \cite[Chapter 2]{HA} is seemingly different from the one we give here,
Haugseng \cite{Haugsengsymseq} and Heine \cite{Hadrianphdthesis} showed that Lurie's model is equivalent to the definition of $\infty$-operads in $\Space$. Hence all the results in $\cite{HA}$ transfer smoothly to the setting of $\infty$-operads in spaces.
\end{remark}

In this paper, we will work exclusively with \emph{non-unital $\infty$-operads}. Roughly speaking, a non-unital $\infty$-operad $\CO$ is an operad without nullary operations.
\begin{definition}
	\label{non-unital operad}
	An $\infty$-operad $\CO$ in $\CC$ is \emph{non-unital} if $\CO(0)$ is equivalent to the zero object of $\CC$. 
\end{definition}

\begin{remark}
\label{Schur functor and operads}
As a consequence of Remark \ref{Schur functor}, the Schur functor $F_\CO$ associated to an operad $\CO$ is a monad on $\CC$.
If additionally we assume $\CC$ is preadditive (Definition \ref{preadditive}) and $\CO$ is a non-unital $\infty$-operad,
then the Schur functor $F_\CQ$ associated to a cooperad $\CQ$ is a comonad on $\CC$ by \cite[Remark 2.21]{Haugsengsymseq}.
\end{remark}

\begin{definition}
	A (non-unital) $\infty$-operad $\CO$ is \emph{connected} \footnote{In \cite{ChingBar}, operads with this property are called reduced. However, the term reduced operads sometimes has another meaning in the literature.} if there is an equivalence $\CO(1)\simeq 1_{\CC}$. 
\end{definition}



% \begin{remark}
% Let $\Fin^{nu}$ be the category of non-empty finite sets.
% Consider the canonical embedding $(\Fin^{nu})^{\simeq}\hookrightarrow \Fin^{\simeq}$. One can then define a \emph{non-unital symmetric sequence in $\CC$}  as a functor 
% \[
% \CO:(\Fin^{nu})^{\simeq}\to \CC.
% \]
% Hence for any symmetric sequence $\CO$ in $\CC$, 
% the underlying non-unital symmetric sequence $\CO_{nu}$ is given by the restriction along $(\Fin^{nu})^{\simeq}\hookrightarrow \Fin^{\simeq}$.
% \end{remark}

% \begin{remark}
% 	Under Lurie's model of $\infty$-operads in $\Space$, a non-unital $\infty$-operad $\CO^{\otimes}$ is defined as an $\infty$-operad whose structure map $\CO^{\otimes} \to \Fin_*$ factors through $\Surj$, where $\Surj$ is the subcategory consisting of surjective maps. 
% 	Note that this is equivalent to our definition in which case $\CO(0)\simeq \emptyset$, the initial object in $\Space$.
% \end{remark}

% No need to make this definition
% \begin{definition}
% \label{non-unitalization of operads}
% 		Let $\CO^{\otimes}$ be an $\infty$-operad in $\Space$, we define (as in \cite{HA}[Definition 5.4.4.1.]) the \emph{non-unitalization of $\CO^{\otimes}$} by $\CO^{\otimes}_{nu}:= \Surj\times_{\Fin_*}\CO^{\otimes}$.
% \end{definition}

% Dually, we define $\infty$-cooperads as coassociative coalgebras in $\SSeq(\CC)$ with respect to the composition product.
% \begin{definition}
% 	\label{infty cooperads}
% 	We define the $\infty$-category $\Coop(\CC):=\Alg(\SSeq(\CC)^{op})^{op}$ of \emph{$\infty$-cooperads in $\CC$} as the opposite $\infty$-category of the $\infty$-category of associtive algebras in of $\SSeq(\CC^{op})$.
% \end{definition}

\begin{definition}
    An \emph{augmentation} of an $\infty$-operad $\CO$ is a map of $\infty$-operads $\epsilon:\CO\rightarrow \triv_{\CC}$ such that $\epsilon\circ \eta\simeq id_{\mathds{1}_\CC}$.
	We call an $\infty$-operad $\CO$ in $\CC$ together with an augmentation $\epsilon$ an \emph{augmented} $\infty$-operad.
% 	% I don't really need it
% 	We will denote the $\infty$-categories of augmented operads and coaugmented cooperads in $\CC$ by $\operatorname{Op}^{aug}(\CC)$ and $\operatorname{coOp}^{aug}(\CC)$, respectively.
\end{definition}


\begin{remark}
A connected $\infty$-operad is augmented with the canonical augmentation $\epsilon:\CO \to \triv_{\CC}$.
\end{remark}  

\begin{remark}
From now on, whenever we say $\infty$-operads (resp. $\infty$-cooperads) we mean non-unital connected $\infty$-operads (resp. $\infty$-cooperads).
\end{remark}

We now introduce two simple examples.
\begin{example}
    	We denote by $\triv_{\CC}$ the symmetric sequence that takes value the tensor unit $1_\CC$ of $\CC$ at $\{*\}$ and the zero object otherwise. One can check that Schur functor $F_{\triv_{\CC}}$ associated to $\triv_{\CC}$ is the identity endofunctor on $\SSeq(\CC)$. Hence $\triv_{\CC}$ serves as a monoidal unit for the composition product in $\SSeq(\CC)$.
	We will refer to $\triv_{\CC}$ as the \emph{trivial $\infty$-operad} in $\CC$.
\end{example}


\begin{example}
\label{Symmetric algebra}
	Consider the \emph{symmetric algebra functor} on $\CC$ defined as 
	\begin{align*}
		\Sym:\CC & \to  \CC\\
		X & \mapsto \amalg_{n\geq 1} (X^{\otimes n})_{h\Sigma_n},
	\end{align*}
	which is the Schur functor of the symmetric sequence $\Com:=(1_\CC,1_\CC,\dots)$, where $1_\CC$ is the tensor unit of $\CC$.
	Since $\Com$ is clearly an associative algebra in $\SSeq(\CC)$ with respect to the 
	composition product, $\Com$ is called the \emph{commutative operad} in $\CC$, and
	$\Sym$ is a monad on $\CC$.
	If we additionally assume $\CC$ is preadditive, then $\Sym$ associated to the symmetric sequence $\Com$ defines a comonad on $\CC$, and we will abuse notation by writing $\Com$ for the commutative cooperad in $\CC$.
% Not necessairly anymore
% 	Similarly, the \emph{non-unital symmetric algebra functor} $\Sym^{\geq 1}:\CC \to \CC$ given by $X\mapsto \amalg_{n\geq 1} (X^{\otimes n})_{h\Sigma_n}$ defines a non-unital $\infty$-operad in $\CC$ which we will denote by $\Com_{nu}$.
\end{example}


\subsection{Truncations of $\infty$-operads}
% \todo{I'm still expecting Gijs' paper for more details to cite in this subsection}
The goal of this subsection is to set up the prerequisites to state Proposition \ref{inductive construction of coalgebras}  \cite[Theorem 4.12]{Heuts_Koszul}, which we will use in the proof of Theorem \ref{2nd Main Theorem}. 
We discuss the notion of truncations of $\infty$-(co)operads, for which we follow the upcoming paper by Heuts \cite{Heuts_Koszul} closely. The upshot of these truncations is to produce natural filtrations on algebras (resp. coalgebras) over operads (resp. cooperads). 


We fix a pointed presentably symmetric monoidal $\infty$-category $\CC$ with tensor product compatible with colimits.
Let $\Fin^{nu}_{\leq n}$ denote the full subcategory of $\Fin^{nu}$ spanned by (non-empty) finite sets with cardinality less or equal to $n$.
We will refer to
$$
\SSeq_{\leq n}(\CC):=\Fun(\Fin^{nu}_{\leq n}, \CC)
$$ 
as the $\infty$-category $\SSeq_{\leq n}(\CC)$ of \emph{$n$-truncated symmetric sequences in $\CC$}.
Restriction along the inclusion $\Fin^{nu}_{\leq n}\to \Fin^{nu}$ induces a
functor 
$$
(-)_{\leq n}: \SSeq(\CC) \to 
\SSeq_{\leq n}(\CC).
$$
which preserves both limits and colimits. 

\begin{lemma}
\label{Compatbility of trancation with composition products}
	\cite[Lemma 2.16]{Hadrianphdthesis}
	If $\CC$ is a pointed symmetric monoidal $\infty$-category with colimits,
	then the restriction functor
$$
(-)_{\leq n}: \SSeq(\CC) \to 
\SSeq_{\leq n}(\CC)
$$
	is compatible with the composition products. Hence it equips a monoidal structure on $\SSeq_{\leq n}(\CC)$ and it lifts to functors between algebras and coalgebras. 

\end{lemma}


We can now define $n$-truncated operads and cooperads in $\CC$.
\begin{definition}
    We define the $\infty$-category of \emph{$n$-truncated operads in $\CC$} as 
    $$
    \operatorname{Op}_{\leq n}(\CC) :=\Alg(\SSeq_{\leq n}(\CC)).
    $$
    Dually, we define 
    $$
     \operatorname{coOp}_{\leq n}(\CC) := \coAlg(\SSeq_{\leq n}(\CC)) 
    $$
    to be the $\infty$-category of \emph{$n$-truncated cooperads in $\CC$}.
\end{definition}

\begin{remark}
	As a consequence of Lemma \ref{Compatbility of trancation with composition products}, there are commutative diagrams
\[
\begin{tikzcd}
%%%% The nodes %%%%%%%%%
	\Opd(\CC)  & 
	\operatorname{Op}_{\leq n}(\CC)\\
	\SSeq(\CC) & \SSeq_{\leq n}(\CC)
%%%% Now the arrows %%%%
	\arrow[from=1-1, to= 1-2, "\rho_n"]
	\arrow[from=1-1, to=2-1, "\oblv" left]
	\arrow[from=1-2, to=2-2, "\oblv'" ]
	\arrow[from=2-1, to= 2-2, "(-)_{\leq n}"]
\end{tikzcd}
\]
and
\[
\begin{tikzcd}
%%%% The nodes %%%%%%%%%
	 \Coop(\CC)  & 
	\operatorname{coOp}_{\leq n}(\CC)\\
	\SSeq(\CC) & \SSeq_{\leq n}(\CC)
%%%% Now the arrows %%%%
	\arrow[from=1-1, to= 1-2, "\rho^n"]
	\arrow[from=1-1, to=2-1, "\oblv" left]
	\arrow[from=1-2, to=2-2, "\oblv'" ]
	\arrow[from=2-1, to= 2-2, "(-)_{\leq n}"].
\end{tikzcd}
\]
where the vertical arrows are forgetful functors.
\end{remark}

We now explain the relations between operads and their truncations, following \cite{Heuts_Koszul}.
Consider the functor 
$$
\zeta_n: \SSeq_{\leq n}(\CC) \to \SSeq(\CC)
$$
given by extending by zero objects in arities above $n$. One can check that it is both left and right adjoint to the restriction functor
$
(-)_{\leq n}.
$


The lemma above has an immediate corollary.
\begin{corollary}
\label{functors between operads adn their truncations}
    The functor 
    $$
    \zeta_n: \SSeq_{\leq n}(\CC) \to \SSeq(\CC)
    $$
    admits both a lax monoidal and an oplax monoidal strucutre. 
\end{corollary}
    The lax monoidal structure on $\zeta_n$ induces a functor on algebras
    $$
    \tau_{n}:\operatorname{Op}_{\leq n}(\CC)
    \to 
    \Opd(\CC)
    $$
    which is right adjoint to $\rho_{n}$. On the other hand, the functor $\rho_n:\Opd(\CC) \to \operatorname{Op}_{\leq n}(\CC)$ preserves limits and filtered colimits (since they are computed in the underlying $\infty$-category of symmetric sequences), hence by the adjoint functor theorem \cite[Corollary 5.5.2.9.]{HTT}, it admits a left adjoint 
    $$
    \varphi_n: \operatorname{Op}_{\leq n}(\CC)
    \to 
    \Opd(\CC).
    $$
    To sum up, we have a diagram consisting of functors described above
\begin{equation}
\label{Op-Op_n adjunction}
	\begin{tikzcd}
	%%%% The nodes %%%%%%%%%
 \Opd(\CC) & \operatorname{Op}_{\leq n}(\CC),
%%%% Now the arrows %%%%
	\arrow[from=1-2, to= 1-1, bend right, shift right = 3, "\varphi_n" above]
	\arrow[from=1-2, to=1-1, bend left, shift left = 3, "\tau_n" below]
	\arrow[from=1-1, to=1-2, "\rho_n"]
\end{tikzcd}
\end{equation}
where the left adjoints are above the right adjoints.
    

    
    Dually, the oplax structure on $\zeta_n$ induces a functor on coalgebras
    $$
    \tau^{n}:\operatorname{coOp}_{\leq n}(\CC)
    \to 
    \Coop(\CC),
    $$
    which is left adjoint to the restriction $\rho^n$. The restriction $\rho^n$ preserves colimits, hence admits a right adjoint
    $$
    \varphi^{n}: \operatorname{coOp}_{\leq n}(\CC)
    \to 
    \Coop(\CC),
    $$
    and we have the following diagram which summarizes the situation for cooperads
    
    \begin{equation}
\label{coOp-coOp_n adjunction}
	\begin{tikzcd}
	%%%% The nodes %%%%%%%%%
\Coop(\CC) & \operatorname{coOp}_{\leq n}(\CC)
%%%% Now the arrows %%%%
	\arrow[from=1-2, to= 1-1, bend right, shift right = 3, "\tau^n" above]
	\arrow[from=1-2, to=1-1, bend left, shift left = 3, "\varphi^n" below]
	\arrow[from=1-1, to=1-2, "\rho^n"].
\end{tikzcd}
\end{equation}


\begin{notation}
	We will abuse notation by writing 
	\begin{itemize}
	    \item 
	    for any operad $\CO$ in $\CC$,
	$\CO \to \tau_{n} \CO$
	for the unit of the bottom adjunction in \eqref{Op-Op_n adjunction} ;
	\item 
	for any operad $\CO$ in $\CC$,
	$
	\varphi_n \CO \to \CO
	$ for the counit of the top adjunction in \eqref{Op-Op_n adjunction} ;
	\item 	for any cooperad $\CQ$ in $\CC$, $\tau^n \CQ \to \CQ$ for the counit of the top adjunction in \eqref{coOp-coOp_n adjunction} ;
	\item 	
	for any cooperad $\CQ$ in $\CC$, 
	$
	\CQ \to \varphi^n \CQ
	$
	for the unit of the bottom adjunction in \eqref{coOp-coOp_n adjunction}.
	\end{itemize}
\end{notation}

We state the following facts from \cite{Heuts_Koszul} without proof.
\begin{fact}
\cite{Heuts_Koszul}
\begin{itemize}
	\item For any $\infty$-operad $\CO$ in $\CC$, there is a sequence of operad maps
	\[
	\varphi_n\CO \to \CO \to \tau_n \CO.
	\]
	The operad $\tau_n\CO$ is the $n$-truncation of $\CO$, i.e., operations of arity higher than $n$ are set to zero.
	The map $\CO \to \tau_n \CO$ is terminal among those operad maps from $\CO$ that are equivalences in arities up to $n$.
	The operad $\varphi_n\CO$ is equivalent to $\CO$ in arities up to $n$, while higher arity operations are "freely generated" by operations of arity less or equal to $n$.
	Hence, the map $\varphi_n\CO \to \CO$ is initial among those operad maps to $\CO$ that are equivalences in arities up to $n$.

	\item Similarly, for any $\infty$-cooperad $\CQ$ in $\CC$, there is a sequence of  cooperad maps
	\[
	\tau^n \CQ \to \CQ \to \varphi^n \CQ.
	\]
	The cooperad $\tau^n\CQ$ is the $n$-truncation of $\CQ$, i.e., cooperations of arity higher than $n$ are set to zero. The map $\CQ \to \varphi^n\CQ$ is terminal among those cooperad maps from $\CO$ that are equivalences in arities up to $n$.
    The cooperad $\varphi^n \CQ$ is "cofreely generated" by cooperations of arities up to $n$.
    The map $\tau^n\CQ \to \CQ$ is initial among those cooperad maps from $\CQ$ that are equivalences in arities up to $n$.
\end{itemize}
\end{fact}

\begin{remark}
	Using the fact above, we see that there is a direct system for an $\infty$-operad $\CO$, 
\begin{equation}
\varphi_1\CO \to \varphi_2\CO \to \cdots \to \CO.
\end{equation}
Similarly, there is an inverse system for the $n$-truncations of $\infty$-operads.
\begin{equation}
\cdots \to 
\tau_2 \CO
\to 
\tau_1 \CO
\to 
\CO
\end{equation}
\end{remark}
%\label{telescope for O_n}
%	\begin{tikzcd}
%	%%%% The nodes %%%%%%%%%
%	\vdots & \\
%	\varphi_3 \CO & \\
%	\varphi_2 \CO & \\
%	\varphi_1 \CO & \CO
%	%%%% Now the arrows %%%%
%	\arrow[from=2-1, to= 1-1]
%	\arrow[from=2-1, to= 4-2]
%	\arrow[from=3-1, to=2-1]
%	\arrow[from=3-1, to=4-2]
%	\arrow[from=4-1, to=3-1]
%	\arrow[from=4-1, to=4-2]
%	\end{tikzcd}


\begin{proposition}
\cite{Heuts_Koszul}
\label{Operad as a colimits}
	If $\CO$ is an $\infty$-operad in $\CC$, 
	then there is an equivalence
	\[
	\CO \simeq
	\colim_n \varphi_n \CO
	\]
	in $\Opd(\CC)$.
\end{proposition}
\begin{proof}
[Sketch of proof:]
    It suffices to check the equivalence aritywise.
    For any arity $k$, the direct system of objects 
    $$
    \varphi_1\CO(k) \to \varphi_2\CO(k) \to \cdots    
    $$
    stabilizes for $n \geq k$.
\end{proof}





\section{Algebras over Operads}
\label{Algebras over Operads}
In this section, we will review the definition of algebras over an $\infty$-operad.
Recall that a symmetric sequence $\CO\in\SSeq(\CC)$ acts on $\CC$ via its Schur functor $F_{\CO}$.
% \[
% \SSeq(\CC)
% \simeq
% \Fun_{\CAlg(\Pr^L)_{\CC/}}(\SSeq(\CC)\SSeq(\CC)).
% \]
If $\CO$ is an $\infty$-operad, then its Schur functor $F_\CO$ is a monad, hence we can consider the $\infty$-category $\LMod_{F_\CO}(\CC)$ of left $F_\CO$-modules in $\CC$.
%\begin{align*}
%SSeq(\CC) \times \CC & \to \CC\\
%(\CO, X)   & \mapsto  \coprod_{n\geq 0} (\CO(n)\otimes X^{\otimes n})_{h\Sigma_n}.
%\end{align*}
\begin{definition}
	\label{algebras over an operad}
	Let $\CO$ be an $\infty$-operad in $\CC$. The $\infty$-category of $\CO$-algebras is $\Alg_{\CO}(\CC):= \LMod_{F_\CO}(\CC)$.
\end{definition}

For a symmetric sequence $A$ in $\CC$, we consider the following \emph{extended power functors}
\begin{equation}
\label{extended power}
    D^{A}_n(X): = (A(n)\otimes X^{\otimes n })_{h\Sigma}, 
\quad
D_{A}^n(X): = (A(n)\otimes X^{\otimes n })^{h\Sigma}.
\end{equation}
Informally, an $\CO$-algebra $X$ in $\CC$ is equipped with maps
$$
D^{\CO}_n(X) \to X
$$
for each $n\geq 1$ and homotopy coherent data that keeps track of the associativity.

\begin{definition}
\label{Def 3.2.2.}
Let $F:\CC\to \CC$ be an endofunctor.
	We define the $\infty$-category $\Alg_{F}(\CC)$ of \emph{$F$-algebras in $\CC$} to be the pullback of the following diagram in $\Cat_{\infty}$
\[
\begin{tikzcd}
%%%% The nodes %%%%%%%%%
	\Alg_{F}(\CC) & 
	\Fun(\Delta^1, \CC)\\
	\CC & 
	\CC \times \CC
%%%% Now the arrows %%%%
	\arrow[from=1-1, to= 1-2]
	\arrow[from=1-1, to=2-1]
	\arrow[from=1-2, to=2-2, "(ev_0\text{,} ev_1)"]
	\arrow[from=2-1, to= 2-2, "(F\text{,} id)"].
\end{tikzcd}
\]
That is, $\Alg_{F}(\CC)$ has objects $X$ of $\CC$ equipped with a morphism $F(X)\to X$.
\end{definition}

\begin{remark}
Our notation might cause potential confusion when $F$ is a monad $T$, since we write $\Alg_T(\CC)$ for the $\infty$-category of left modules over $T$. Note that this is different from the pullback definition in Definition \ref{Def 3.2.2.}. 
\end{remark}

Proposition \ref{Operad as a colimits} motivates us to ask the following question: Can we write an $\CO$-algebra, as the limit of $\varphi_k\CO$-algebras as in the case of Postnikov decomposition of a simply-connected space? 

Heuts answers this question in the following theorem.
\begin{theorem}
\cite[Theorem 4.1]{Heuts_Koszul}
\label{Thm 4.1 of Heuts Koszul Duality paper}
For each $n \geq 2$, the commutative square of $\infty$-categories
\[
\begin{tikzcd}
%%%% The nodes %%%%%%%%%
	\Alg_{\varphi_n\CO}(\CC) & 
	\Alg_{D^{\CO}_{n}}(\CC)\\
	\Alg_{\varphi_{n-1}\CO} (\CC)  & 
	\Alg_{D_{n}^{\varphi_{n-1}\CO}}(\CC)
%%%% Now the arrows %%%%
	\arrow[from=1-1, to= 1-2]
	\arrow[from=1-1, to=2-1]
	\arrow[from=1-2, to=2-2]
	\arrow[from=2-1, to= 2-2].
\end{tikzcd}
\]
is a pullback square. Furthermore, the natural map
$$
\operatorname{Alg}_{\mathcal{O}}(\mathrm{C}) \rightarrow \lim _{n} \operatorname{Alg}_{\varphi_{n} \mathcal{O}}(\mathcal{C})
$$
is an equivalence of $\infty$-categories.
\end{theorem}

\begin{remark}
Heuts stated Theorem \ref{Thm 4.1 of Heuts Koszul Duality paper} for a stable $\infty$-category, but a careful examination of the proof shows that the theorem holds for a presentably symmetric monoidal $\infty$-category $\CC$, which is our assumption throughout this chapter.
\end{remark}

\begin{remark}
Theorem \ref{Thm 4.1 of Heuts Koszul Duality paper} has the following informal interpretation: suppose $X$ is a $\varphi_{n-1}\CO$-algebra, then to specify a $\varphi_n\CO$-algebra structure on $X$, it suffices to equip $X$ with a multiplication map $\mu_n: D^{\CO}_n(X)\to X$ that is compatible with the $\varphi_{n-1}\CO$-algebra structure maps. We refer the readers to \cite{Heuts_Koszul} for further details.
\end{remark}





\section{Koszul Duality and Divided Power Conilpotent  Coalgebras }
\label{Coalgebras over cooperads and Koszul Duality}
In this section, we discuss Koszul duality for operads in the sense of \cite{Ginzburg-Kapranov} and define divided power, conilpotent coalgebras over an $\infty$-cooperad. 
We will assume $\CC$ is a presentably stable, symmetric monoidal $\infty$-category in this section.

We first discuss bar-cobar duality between $\infty$-operads and $\infty$-cooperads. The general form of bar-cobar duality is exhibited in the form of associative algebras and coassociative coalgebras in a nice $\infty$-category in \cite{HA}.
\begin{proposition}
\cite[Remark 5.2.2.19.]{HA}
Let $\CD$ be a pointed monoidal $\infty$-category admitting geometric realizations of simplicial objects and totalizations of cosimplicial objects. Then there is an adjunction
\[
\adj{B}{\Alg^{\operatorname{aug}} (\CD)}{\coAlg^{\operatorname{aug}}(\CD)}{C}.
\]
\end{proposition}
If $\CD= \SSeq(\CC)$, then we obtain an adjunction between (augmented) operads and (coaugmented) cooperads.
	$$
	\adj{B}{\Opd^{aug}(\CC)}{\Coop^{aug}(\CC)}{C}.
	$$
Explicitly, the bar construction $B\CO$ of an $\infty$-operad $\CO$ is computed as the geometric realization of the simplicial bar construction with respect to the composition products \cite[Section 4.4.2]{HA}
	\[
		\Barconstruction(\triv, \CO, \triv)_{\bullet}:=\xymatrix{ \mathds{1}\ar@<0ex>[r]  &  
		\CO \ar@<1ex>[r] \ar@<-1ex>[r] \ar@<1ex>[l] \ar@<-1ex>[l]  &  \CO\circ \CO \ar@<2ex>[l] \ar@<0ex>[l] \ar@<-2ex>[l] \cdots},
\]
and we will write 
$$
B\CO := |\Barconstruction(\triv, \CO, \triv)_{\bullet}|.
$$
	Similarly, the cobar construction $C\CQ$ of a cooperad $\CQ$ is computed as the totalization of the cosimplicial object
	\[
		\Cobar(\triv, \CQ, \triv)^{\bullet}:=\xymatrix{ \mathds{1} \ar@<1ex>[r] \ar@<-1ex>[r] &  
		\CQ \ar@<0ex>[l] \ar@<2ex>[r] \ar@<0ex>[r] \ar@<-2ex>[r] & \CQ\circ \CQ \ar@<1ex>[l] \ar@<-1ex>[l] \cdots}.
\]
and we will write 
$$
C\CQ := \Tot \Cobar(\triv, \CQ, \triv)^{\bullet}.
$$



\begin{definition}
	An $\infty$-operad $\CO\in \Opd^{aug}(\CC)$ is \emph{Koszul} if the unit map
	$$
	\CO\rightarrow CB(\CO)
	$$
	is an equivalence.
\end{definition}

If we restrict to $\infty$-operads in a stable $\infty$-category $\CC$, then every connected $\infty$-operad is Koszul.

\begin{proposition}
\cite[Proposition 3.4]{Heuts_Koszul}
\label{Connected operads are Koszul}
Let $\CC$ be a presentably stable symmetric monoidal $\infty$-category. Then the bar-cobar adjunction
	$$
	\adj{B}{\Opd^{aug}(\CC)}{\Coop^{aug}(\CC)}{C}.
	$$
	restricts to an equivalence on the  $\infty$-categories of connected operads and cooperads.
\end{proposition}


We now introduce functors that will play important roles throughout the rest of the thesis. 
Let $\CO$ be a connected $\infty$-operad with its canonical augmentation $\epsilon:\CO\rightarrow \mathds{1}$.
Restriction along $\epsilon$ induces a functor 
$$
\trivial_{\CO}: \CC\simeq\Alg_{\mathds{1}}(\CC)\rightarrow \Alg_{\CO}(\CC),
$$
which we will call the \emph{trivial $\CO$-algebra functor}.
The trivial $\CO$-algebra functor admits a left adjoint $\cot_{\CO}:\CC\rightarrow \Alg_{\CO}(\CC)$ given by the relative tensor product $\triv\circ_{\CO}(-)$, whose existence can also be deduced from the adjoint functor theorem \cite[Corollary 5.5.2.9.]{HTT}. 
The functor $\cot_{\CO}$ is called the \emph{cotangent fiber functor} in \cite{Heuts_Koszul}. 
\begin{remark}
Informally, a trivial $\CO$-algebra $X$ is an $\CO$-algebra whose structure map 
$(\CO(n)\otimes X^{\otimes n})_{h\Sigma_n}\to X$ factors through $0$ when $n>1$.
\end{remark}

\begin{remark}
If $\CO$ is the commutative operad, the functor $\cot_{\CO}$ is often called \emph{Topological Andr\'e-Quillen homology} in the literature. 
The choice of the terminology from \cite{Heuts_Koszul}
comes from the following fact.
Let $\CC$ be the category of chain complexes over a commutative ring $k$ and $\CO$ the non-unital commutative operad. If $A$ is a commutative $k$-algebra, then $\cot_{\CO}(A)$ computes the fiber of the cotangent complex $L_{A/k}$ at the $k$-point of $\operatorname{Spec}(A)$ determined by the augmentation of $A$.
\end{remark}


Similarly, restriction along the unit map $\eta:\mathds{1}\rightarrow \CO$ induces a functor
$$
\oblv_{\CO}: \Alg_{\CO}(\CC)
\rightarrow 
\CC\simeq\Alg_{\mathds{1}}(\CC),
$$
which we will refer as the \emph{$\CO$-forgetful functor}.
The $\CO$-forgetful functor admits a left adjoint $\Free_{\CO}:\CC\rightarrow \Alg_{\CO}(\CC)$ given by $\CO\circ (-)$ which we will call the \emph{free $\CO$-algebra functor}.
    
The composite
$$
\mathds{1}\xrightarrow{\eta} \CO \xrightarrow{\epsilon} \mathds{1}
$$
is equivalent to the identity, hence we have equivalences
$$
\cot_{\CO} \circ \Free_{\CO} \simeq \id
$$
and 
$$
\oblv_{\CO}\circ \trivial_{\CO} \simeq \id.
$$
The situation can be summarized in the following diagram of adjunctions
\[
\begin{tikzcd}
	%%%% The nodes %%%%%%%%%
\CC & \Alg_{\CO}(\CC) & \CC
%%%% Now the arrows %%%%
	\arrow[from=1-1, to= 1-2, shift left = 1, "\Free_{\CO}" above]
	\arrow[from=1-2, to=1-1, shift left = 1, "\oblv{\CO}" below]
	\arrow[from=1-2, to= 1-3, shift left = 1, "\cot_{\CO}" above]
	\arrow[from=1-3, to=1-2, shift left = 1, "\trivial_{\CO}" below]
\end{tikzcd}
\]
in which the left adjoints are above their right adjoints and both horizontal composites are equivalent to the identity functor.

The following corollary of the Barr-Beck-Lurie theorem \cite[Theorem 4.7.3.5.]{HA} says that any $\CO$-algebra $X$ is canonically equivalent to the geomectric realization of a simplicial object of $\CO$-algebras.
\begin{proposition}
\label{free resolutino of O-algebras}
If $X$ is an $\CO$-algebra, then it can be resolved as the geometric realization of the simplicial objects $(\Free_{\CO}\circ \oblv_{\CO})_{\bullet + 1}X$, i.e., 
\begin{equation}
\label{(3.5)}
    X \simeq
|(\Free_{\CO}\circ \oblv_{\CO})_{\bullet + 1}X|
\simeq |\Barconstruction(\CO, \CO, X)_{\bullet}|.
\end{equation}
\end{proposition}
\begin{proof}
    This follows from the fact that the adjunction $(\Free_{\CO}, \oblv_{\CO})$ is monadic and Corollary \ref{Cor of Barr-Beck-Lurie theorem}.
    
\end{proof}
Applying $\cot_{\CO}$ to both sides of \eqref{(3.5)} yields a formula for computing the cotangent fiber of $X$. 
\begin{corollary}
\cite[Proposition 4.4]{Heuts_Koszul}
The cotangent fiber of an $\CO$-algebra $X$ can be computed as 
$$
\cot_{\CO}X \simeq 
|(\oblv_{\CO}\circ \Free_{\CO})_{\bullet}\oblv_{\CO}X|,
$$
where the geometric realization is computed in the underlying $\infty$-category $\CC$.
\end{corollary}

As a consequence, we can identify the comonad $\cot_{\CO}\circ \trivial_{\CO}$ in terms of the bar construction of $\CO$.
\begin{proposition}
\label{cot triv is F_BO}
\cite[Proposition 4.5]{Heuts_Koszul}
The comonad $\cot_{\CO}\circ \trivial_{\CO}$ is naturally equivalent to the comonad $F_{B\CO}$ associated with the cooperad $B\CO$.
\end{proposition}

We are now ready to define the $\infty$-category of divided power, conilpotent coalgebras over an $\infty$-cooperad.
\begin{definition}
\label{coalgebras over a cooperad}
	Let $\CQ$ be an $\infty$-cooperad in $\CC$. We define the $\infty$-category of divided power, conilpotent coalgebras over a cooperad $\CQ$ as the $\infty$-category of left comodules over $F_{\CQ}$,
	$$
	\coAlg^{\divpow, \nil}_{\CQ}(\CC):= \operatorname{LcoMod}_{F_{\CQ}}(\CC).
	$$
\end{definition}

Analogous to the case of algebras over an operad, we have two pairs of adjunctions 
\[
\begin{tikzcd}
%%%% The nodes %%%%%%%%%
\CC & \coAlg^{\divpow, \nil}_{\CQ}(\CC) & \CC
%%%% Now the arrows %%%%
	\arrow[from=1-1, to= 1-2, shift left = 1, "\cofree^{\nil}_{\CQ}" above]
	\arrow[from=1-2, to=1-1, shift left = 1, "\oblv^{\nil}_{\CQ}" below]
	\arrow[from=1-2, to= 1-3, shift left = 1, "\operatorname{Prim}^{\nil}_{\CQ}" above]
	\arrow[from=1-3, to=1-2, shift left = 1, "\trivial^{\nil}_{\CQ}" below]
\end{tikzcd}
\]
where the right adjoints are above the left adjoints,
and compositions of the horizontal functors are equivalent to the identity functor on $\CC$.

Moreover, by an argument dual to the proof of Proposition \ref{free resolutino of O-algebras}, we can resolve any divided power, conilpotent coalgebra by a totalization of cosimplicial cofree coalgebras.
\begin{proposition}
Let $X$ be a divided power, conilpotent $\CQ$-coalgebra, then it can be resolved as the totalization of the cosimplicial object $(\cofree_{\CQ}\circ \oblv_{\CQ})^{\bullet + 1}X$, i.e. 
\begin{equation}
\label{(3.6)}
    X \simeq
\Tot (\cofree_{\CQ}\circ \oblv_{\CQ})^{\bullet + 1}X
\simeq \Tot \Cobar(\CQ, \CQ, X)^{\bullet}.
\end{equation}
\end{proposition}



The functor $\cot_{\CO}$ factors through the $\infty$-category $\LcoMod_{\cot_{\CO}\circ \trivial_{\CO}}(\CC)$ of left comodules over the comonad $(\cot_{\CO}\circ \trivial_{\CO})$, which can be identified with the $\infty$-category of left comodules over the comonad $F_{B\CO}$ by Proposition \ref{cot triv is F_BO}, hence we can write the resulting factorization as
\[
\begin{tikzcd}
     \Alg_{\CO}(\CC) &   & 
     \CC\\
                     & \coAlg^{\divpow, \nil}_{B\CO}(\CC) &
    \arrow[from = 1-1, to = 1-3, "\cot_{\CO}"]
    \arrow[from = 1-1, to = 2-2, "\indec_{\CO}" below, outer sep=3pt]
    \arrow[from = 2-2, to = 1-3, "\oblv_{B\CO}^{\nil}" below, outer sep=3pt].
\end{tikzcd}
\]
% The functor $\indec_{\CO}$ can be computed explicitly as 
% \begin{align*}
%     \indec_{\CO}(X) &  \simeq \indec_\CO  
%     |(\Free_{\CO}\circ \oblv_{\CO})_{\bullet + 1}X|\\
%     & \simeq | \indec_{\CO}\circ \Free_{\CO} (F_{\CO})_{\bullet} \oblv_{\CO}X |\\
%     & \simeq |\trivial_{B\CO} (F_{\CO})_{\bullet} \oblv_{\CO}X  |.
% \end{align*}
The functor $\indec_{\CO}$ preserves colimits, hence it admits a right adjoint $\Prim^{\nil}_{B\CO}$ by the adjoint functor theorem \cite[Corollary 5.5.2.9.]{HTT}, which we will call the \emph{primitives functor};
for $Y \in \coAlg^{\divpow, \nil}_{B\CO}(\CC)$, the \emph{primitives} $\Prim_{B\CO}^{\nil}(Y)$ of $Y$ can be computed explicitly as \cite[Lemma 4.7]  {Heuts_Koszul}
$$
\Prim_{B\CO}^{\nil}(Y) \simeq \Tot \trivial_{\CO} (F_{B\CO})^{\bullet} \oblv^{nil}_{B\CO} (Y).
$$

% I don't need this anymoree
% We now introduce other types of coalgebra over a cooperad $\CQ$. 
% As the dual notion of algebras over operad, one would expect a colagebra $X$ over a cooperad $\CQ$ to be an object $X$ in $\CC$ equipped with maps
% $$
% \epsilon_n: X \to  (\CQ(n) \otimes X^{\otimes n})^{h\Sigma_n}
% $$
% that are homotopy-coherently coassociative. Recall we have defined a cooperad $\CQ$ to be a comonoid in $\SSeq(\CC)$ with respect to the composition product, hence it's a monoid in $\Fun(\CC^{op}, \CC^{op})$. 
% \begin{definition}
%     \label{coalgebras over cooperads}
%     We define the $\infty$-category of \emph{coalgebras over the cooperad $\CQ$} to be 
%     $$
%     \coAlg_{\CQ}(\CC) := \Alg_{\CQ}(\CC^{op})^{op}.
%     $$
% \end{definition}
For future application, we record the following lemma.
\begin{lemma}
\cite[(3.4) and (3.5)]{Francis-Gaitsgory}
\label{CE of Trivial is cofree}
There are equivalences
$$
\indec_{\CO}\circ\trivial_{\CO} \simeq \cofree^{\nil}_{B\CO}  \text{ and } 
\Prim_{B\CO}^{\nil} \circ \cofree^{\nil}_{B\CO} \simeq \trivial_{\CO}.
$$
\end{lemma}
\begin{proof}
    The first equivalence is a direct consequence of Proposition \ref{cot triv is F_BO}.
    The composite $\Prim_{B\CO}^{\nil} \circ \cofree^{\nil}_{B\CO}$ is right adjoint to
    $\oblv{_{\CO}\circ \indec_{\CO}}\simeq \cot_{\CO}$, hence $\Prim_{B\CO}^{\nil} \circ \cofree^{\nil}_{B\CO} \simeq \trivial_{\CO}$.
\end{proof}



We also have the following decomposition result for divided power conilpotent $\CQ$-coalgebras, which will be used in the proof of the essential surjectivity of the functor $C_{\operatorname{tame}}$. Let $\CQ$ be a connected $\infty$-cooperad.
\begin{proposition}
\cite[Theorem 4.12]{Heuts_Koszul}
\label{inductive construction of coalgebras}
    For $n\geq 2$, the following commutative square of $\infty$-categories 
\[
\begin{tikzcd}
%%%% The nodes %%%%%%%%%
	\coAlg_{\varphi^n \CQ}(\CC) & 
	\coAlg_{D^n_{\CQ}}(\CC)\\
	\coAlg_{\varphi^{n-1} \CQ}(\CC) & 
	\coAlg_{D^n_{\varphi^{n-1}\CQ}}(\CC)
%%%% Now the arrows %%%%
	\arrow[from=1-1, to= 1-2]
	\arrow[from=1-1, to=2-1]
	\arrow[from=1-2, to=2-2]
	\arrow[from=2-1, to= 2-2]
\end{tikzcd}
\]
is a pullback square. Moreover, the natural map
$$
\coAlg_{\CQ}(\CC) \to \lim_n \coAlg_{\varphi^n\CQ}(\CC)
$$
is an equivalence.
\end{proposition}


\section{The spectral Lie operad}
\label{The spectral Lie operad}
In this section, we introduce an operad in $\Sp$ which will be central to this thesis. 
We first need to provide some background on partition posets. 
Consider the set $\mathbf{P}(n)$ of partitions (i.e., equivalence relations) on the finite set $\{1, \cdots, n \}$. $\mathbf{P}(n)$ is a poset with minimal element the trivial partition and maximal element the discrete partition.
Write $\mathbf{P}^{+}(n)$ (resp. $\mathbf{P}^{-}(n)$ ) for the subposet of $\mathbf{P}(n)$ obtained by deleting the minimal (resp. maximal) partition.

    Goodwillie calculus is an important tool in homotopy theory, we will assume basic familiarity of its theory and applications. The survey paper \cite{Aone-Ching_Survey} is an excellent source on this subject.
	The Goodwillie derivative $\partial_* \id$ of the identity functor $\id: \Space_* \to \Space_*$ forms a symmetric sequence in $\Sp$, i.e., each $\partial_n \id$ is a $\Sigma_n$-spectrum in the naive sense. In \cite{JohnsonDerivative} and \cite{Arone-Mahowald}, it was shown that
	$$
	\partial_n \id \simeq \BD(\Sigma^{\infty} K_n),
	$$
	where 
	$
	K_{n}:=|\mathbf{P}(n)| /\left(\left|\mathbf{P}^{+}(n)\right| \cup\left|\mathbf{P}^{-}(n)\right|\right)
	$
	and $\BD$ denotes the Spanier-Whitehead dual. 
	Let $\Com$ denote the commutative cooperad in $\Sp$.
	Ching \cite{ChingBar} identified the derivatives of the identity functor as the cobar construction of the commutative cooperad and hence admits an operad structure.
	\begin{remark}
	We remark that Ching works with point-set models of operads in spectra. However, one can choose a simplicial model for the operads in \cite{Ching_Bar-cobar} and apply operadic nerve \cite[Definition 2.1.1.23.]{HA}
	to obtain relevant results for $\infty$-operads.
	The operad $\partial_* \id$ is the cobar construction of the commutative cooperad in $\Sp$ (\cite[Remark 8.9]{ChingBar})
	$$
	\Cobar(\Com)\simeq \partial_* \id.
	$$
	\end{remark}
	
	\begin{remark}
    Classical Koszul duality between the Lie operad and the commutative cooperad $\Com$ in (graded) abelian groups is studied in \cite{Ginzburg-Kapranov} and \cite{Loday-Vallette};
    there is an equivalence of operads in (graded) abelian groups
    \[
    \Lie[-1] \simeq \Com^{\vee}
    \]
    where $\Com^{\vee}$ denotes the linear dual of the commutative cooperad and $\Lie[-1](n)_p:=\Lie(n)_{p+1}$.
    \end{remark}
    
	\begin{definition}
	\label{Shifted Spectral Lie Operad}
	    	We define the \emph{shifted spectral Lie operad} to be
	    	$$
	    	\BL:= \partial_* \id.
	    	$$
	\end{definition}

	The name comes from the following computation in \cite[Example 9.50]{ChingBar},
	$$
	H_{*}\BL(n) \cong 	
	\begin{cases}
	\Lie(n) \otimes \operatorname{sgn}& \text{ if $*=1-n$},\\
	0 & \text{otherwise}
	\end{cases}
	$$	
	where $\operatorname{sgn}$ denotes the sign representation.


The mismatch of degrees between the spectral Lie operad $\BL$ and the Lie operad $\Lie$ in abelian groups is rather inconvenient for applications. To remedy this, we recall a shift operation for $\infty$-operads in $\Sp$ introduced in \cite[\S 2.2.4.]{Hadrianphdthesis} and \cite[Section 3]{Camarena_mod2_free_spectral_Lie_algebra}.
\begin{definition}
    Suppose there is an adjunction
    $$\adj{L}{\Sp}{\CC}{R}$$
    for some $\infty$-category $\CC$. Let $T$ be the monad arising from this adjunction, then the \emph{desuspended monad} $\Omega T \Sigma$ is a monad on $\Sp$ and we denote it by
     $\mathbf{\Sigma}^{-1}  T$.
	If the monad $T$ is the Schur functor $F_{\CO}$ of an $\infty$-operad $\CO$, then there is a \emph{desuspended operad} $\Sigma^{-1}\CO$ corresponding to the monad $\mathbf{\Sigma}^{-1} F_{\CO}$, which has underlying symmetric sequence 
	$$
	(\mathbf{\Sigma^{-1}} \CO ) (n)= \BS^{n}\otimes\Sigma^{-1} \CO(n)
	$$
	where $\Sigma_n$ acts on $\BS^{n}$ by permuting the $n$ factors of $\BS^{1}$, and $\Sigma_n$ acts on $\mathbf{\Sigma^{-1}} \CO(n)$ via the its action on $\CO(n)$.
\end{definition}

We now state some results concerning shifts of monads and $\infty$-operads without proof. We refer the reader to \cite[Section 2.2.4.]{Hadrianphdthesis} and \cite{Camarena_mod2_free_spectral_Lie_algebra} for more details.
The following lemma indicates that shifting an $\infty$-operad is indeed harmless to the category of algebras we want to study.
\begin{lemma}
\cite[Section 2.2.4.]{Hadrianphdthesis}
\label{Shift has no harm}
Let $\CC$ be a stable $\infty$-category.
There is a pullback diagram
\[
    \begin{tikzcd}
	\Alg_{\bf{\Sigma}^{-1} \CO }(\CC)    & \Alg_{\CO}(\CC) \\
	 \CC & \CC
	\arrow[from=1-1, to = 1-2, "\Sigma'", "\simeq" below]
	\arrow[from=1-1 , to =2-1,  left]
	\arrow[from=1-2 , to =2-2,  right]
	\arrow[from=2-1, to=2-2, "\Sigma", "\simeq" below].
\end{tikzcd}
\]
of $\infty$-categories.
\end{lemma}
As a consequence, we write  
$$
\Omega':
\Alg_{\CO}(\CC) \to \Alg_{\bf{\Sigma}^{-1} \CO }(\CC)
$$
for the inverse of $\Sigma'$,
which fits into a commutative diagram
\[
    \begin{tikzcd}
	\Alg_{\CO}(\CC)    & \Alg_{\bf{\Sigma}^{-1} \CO }(\CC) \\
	 \CC & \CC
	\arrow[from=1-1, to = 1-2, "\Omega'", "\simeq" below]
	\arrow[from=1-1 , to =2-1,  left]
	\arrow[from=1-2 , to =2-2,  right]
	\arrow[from=2-1, to=2-2, "\Omega", "\simeq" below].
\end{tikzcd}
\]

Moreover, 
we have two commutative diagrams of right adjoints
\begin{equation}
    \label{trivial commutes with shifts}
    \begin{tikzcd}
	\Alg_{\CO}(\CC)    & \Alg_{\bf{\Sigma}^{-1} \CO }(\CC) \\
	 \CC & \CC
	\arrow[from=1-1, to = 1-2, "\Omega'", "\simeq" below]
	\arrow[from=2-1 , to =1-1, "\trivial_{\CO}" left]
	\arrow[from=2-2 , to =1-2,  "\trivial_{\bf{\Sigma}^{-1} \CO }" right]
	\arrow[from=2-1, to=2-2, "\Omega", "\simeq" below],
\end{tikzcd}
\end{equation}
and 
\begin{equation}
    \label{diagram of equivalences in shifting}
    \begin{tikzcd}
	\Alg_{\CO}(\CC)    & \Alg_{\bf{\Sigma}^{-1} \CO }(\CC) \\
	 \Alg_{\CO}(\CC) & \Alg_{\bf{\Sigma}^{-1} \CO }(\CC)
	\arrow[from=1-1, to = 1-2, "\Omega'", "\simeq" below]
	\arrow[from=1-1 , to =2-1, "\Omega_{\CO}" left]
	\arrow[from=1-2 , to =2-2, "\Omega_{\mathbf{\Sigma}^{-1} \CO}" right]
	\arrow[from=2-1, to=2-2, "\Omega'", "\simeq" below],
\end{tikzcd}
\end{equation}
where $\Omega_{\CO}$ and $\Omega_{\mathbf{\Sigma}^{-1} \CO}$ denote the loop functor in $\Alg_{\CO}(\CC)$ and $\Alg_{\bf{\Sigma}^{-1} \CO }(\CC) $, respectively.
The commutativity of (\ref{trivial commutes with shifts}) follows from the fact that $\Omega' \circ \trivial_{\CO}$ and $\trivial_{\bf{\Sigma}^{-1} \CO }\circ \Omega$ are right adjoint to $ \cot_{\CO}\circ \Sigma'$ and $\Sigma \circ \cot_{\bf{\Sigma}^{-1} \CO}$, respectively; and there are equivalences
\begin{align*}
    \cot_{\CO}\circ (\Sigma' X) & \simeq |(F_{\CO})_{\bullet} (\Sigma X)|\\
    & \simeq |\Sigma (\Omega F_{\CO}\Sigma)_{\bullet} (X) |\\
    & \simeq \Sigma \cot_{\bf{\Sigma}^{-1} \CO}
\end{align*}
where we used that there is an equivalence of simplicial objects
$$
\Sigma (\Omega F_{\CO}\Sigma)_{\bullet} (X)
\to
(F_{\CO})_{\bullet} (\Sigma X) 
$$
in the second equivalence.

The commutativity of (\ref{trivial commutes with shifts}) says that applying $\Omega'$ to a trivial $\CO$-algebra gives rise to a trivial $\bf{\Sigma}^{-1} \CO$-algebra, and the commutativity of (\ref{diagram of equivalences in shifting}) says that there is an equivalence $\Omega_{\bf{\Sigma}^{-1} \CO}X \simeq \Omega'\circ \Omega_{\CO}(\Sigma' X)$ for $X\in \Alg_{\bf{\Sigma}^{-1} \CO}(\CC)$.
Therefore, we obtain the following lemma.
\begin{lemma}
\label{transition of triviality}
Let $Y\in \Alg_{\bf{\Sigma}^{-1} \CO}(\CC)$.
If $\Omega_{\CO}(\Sigma' Y)$ is a trivial $\CO$-algebra, then
$\Omega_{\bf{\Sigma}^{-1} \CO}Y$ is a trivial $\bf{\Sigma}^{-1} \CO$-algebra.
\end{lemma}
\begin{proof}
    By the assumption, $\Omega_{\CO}(\Sigma' Y)$ is a trivial $\CO$-algebra, i.e. $\Omega_{\CO}(\Sigma' Y)\simeq \trivial_{\CO}Y$.
    Moreover, by the commutativity of (\ref{trivial commutes with shifts}) and (\ref{diagram of equivalences in shifting}), there are equivalences 
    $$
    \Omega_{\bf{\Sigma}^{-1} \CO}Y \simeq \Omega' \Omega_{\CO}(\Sigma' Y)
    \simeq 
    \Omega'\trivial_{\CO}(Y)
    \simeq \trivial_{\bf{\Sigma}^{-1} \CO}(\Omega Y).
    $$
\end{proof}

% By Proposition \ref{Prop 2.8 GMN} and Corollary \ref{Alg(C) equivalent to groups in Alg(C)}, the composite
% $$
% \Alg_{\CO}(\CC) \xrightarrow{\Omega_{\CO}} 
% \Grp(\Alg_{\CO}(\CC))
% \xrightarrow{\oblv_{\CO}}
% \Alg_{\CO}(\CC)
% $$
% is an equivalence of $\infty$-categories.
% We abuse notation by still writing $\Omega_{\CO}$ as the composition above.
% Therefore, we have a commutative diagram of equivalences
\begin{construction}
[Suspension morphism]

Consider the commutative diagram
\[
\begin{tikzcd}
     \Alg_{\CO}(\CC) &   & \CC\\
                     & \Alg_{\CO}(\CC) &
    \arrow[from = 1-1, to = 1-3, "\oblv_{\CO}\circ \Omega_{\CO}"]
    \arrow[from = 1-1, to = 2-2, "\Omega_{\CO}" ]
    \arrow[from = 2-2, to = 1-3, "\oblv_{\CO}"].
\end{tikzcd}
\]
The forgetful functor $\oblv_{\CO}$ is monadic and it corresponds to the monad $F_{\CO}$. Since the functor $\oblv_{\CO}\circ \Omega_{\CO}$ is conservative and preserves sifted colimits, it is also monadic by the Barr-Beck-Lurie theorem \cite[Theorem 4.7.3.5.]{HA}. Moreover, the monad induced from the right adjoint $\oblv_{\CO}\circ \Omega_{\CO}$ and its left adjoint $\Sigma_{\CO}\circ \Free_{\CO}$ is exactly $F_{\bf{\Sigma}^{-1} \CO}$; indeed, the monad arising from this adjunction is given by
$$
\oblv_\CO  \Omega_\CO \Sigma_\CO \Free_\CO \simeq \Omega \oblv_{\CO}\Free_{\CO} \Sigma
\simeq \Omega F_{\CO} \Sigma,
$$
where we use that $\Free_{\CO}$ preserves colimits so $\Sigma_{\CO} \Free_{
CO}\simeq \Free_{\CO} \Sigma$.
Therefore, we obtain a functor 
$$
\sigma^{*}: \Alg_{\bf{\Sigma}^{-1} \CO }(\CC) 
\to 
\Alg_{\CO}(\CC)
$$
which is the dashed arrow in the following commutative diagram
\[
\begin{tikzcd}
     \Alg_{\CO}(\CC) &   & \CC \\
                     &   &      \\
                     & \Alg_{\bf{\Sigma}^{-1} \CO }(\CC)  & \\
                     &   & \\
                     & \Alg_{ \CO }(\CC) 
    \arrow[from = 1-1, to = 1-3, "\oblv_{\CO}\circ \Omega_{\CO}"]
    \arrow[from = 1-1, to = 3-2, "\Omega'"]
    \arrow[from = 3-2, to = 1-3, "\oblv_{\bf{\Sigma}^{-1} \CO }"]
    \arrow[from = 1-1, to = 5-2, "\Omega_{\CO}" left , bend right]
    \arrow[from = 5-2, to = 1-3, "\oblv_{\CO}" right , bend right]
    \arrow[from = 3-2, to = 5-2, "\sigma^{*}", dashed]
    .
\end{tikzcd}
\]
By the dual statement of Theorem \ref{Monads-Alg correspondence}, the functor 
$$
\sigma^{*}:
 \Alg_{\bf{\Sigma}^{-1} \CO }(\CC)\to \Alg_{\CO}(\CC)
$$
induces a map of monads
\begin{equation}
\label{suspension morphism}
    \sigma: F_{\CO}\to \Omega F_{\CO}\Sigma, 
\end{equation}
which we will refer as the \emph{suspension morphism} associated to the operad $\CO$.
\end{construction}





% \begin{lemma}
% \label{Shift has no harm}
%     The functor $\Sigma': \Alg_{\bf{\Sigma}^{-1} \CO }(\CC) \to \Alg_{\CO }(\CC)$ is an equivalence of $\infty$-categories.
% \end{lemma}
% \begin{proof}
% 	Consider the commuting diagram
% \[
% \begin{tikzcd}
% 	\Alg_{\bf{\Sigma}^{-1} \CO }(\CC) &   & \Alg_{\CO}(\CC) \\
% 	& \CC &
% 	\arrow[from=1-1, to = 1-3, "\Sigma'"]
% 	\arrow[from=1-1 , to =2-2, "\Sigma \circ  \oblv_{\bf{\Sigma}^{-1}\CO}" left]
% 	\arrow[from=1-3, to=2-2, "\oblv_{\CO}"].
% \end{tikzcd}
% \]
% We want to check the conditions of \cite{HA}[Corollary 4.7.3.16.].
% Conditions (1), (2), (3) are immediate since both diagonal arrows in the diagram above are conservative, hence we are left to check (5).
% Consider the map 
% \[
% \varphi: \Free_{\CO}(X) \to \Sigma' 
% \circ \Free_{\bf{\Sigma}^{-1}\CO} (\Sigma^{-1} X)
% \]
% that is left adjoint to
% \[
% X \to 
% \oblv_{\CO} 
% \circ
% \Sigma' 
% \circ\Free_{\bf{\Sigma}^{-1}\CO} (\Sigma^{-1} X),
% \]
% and we want to check $\varphi$ is an equivalence for any $X\in \CC$.
% Note that $\varphi$ is induced from the map of monads 
% % By Theorem \ref{Monads-Alg correspondence}, 
% % it suffices to check the induced map on monads
% $$
% F_{\CO} \to \Sigma\Omega F_{\CO} \Sigma \Omega,
% $$
% which is an equivalence because we assume $\CC$ is stable.

% % \[
% % \oblv_{\mathbf{\Sigma}\CO}(\varphi):
% % \mathbf{\Sigma}\CO(X) \to 
% % \oblv_{\mathbf{\Sigma}\CO} \circ \Omega'\circ \Free_{\CO} (\Sigma X)
% % \]
% % is an equivalence, where the latter is equivalent to 
% % $$
% % \Omega \circ \oblv_{\CO}\circ \Free_{\CO}(\Sigma X)\simeq \mathbf{\Sigma}\CO(X),
% % $$
% % and the proof is now complete.
% \end{proof}

\begin{definition}
	\label{spectral Lie operad}
	We define the \emph{spectral Lie operad} as $$
	\spLie := \mathbf{\Sigma}^{-1} \BL.
	$$
\end{definition}

\begin{remark}
\label{Remark on shifted Lie operads}
The underlying symmetric sequence of the spectral Lie operad $\spLie:= \mathbf{\Sigma}^{-1}\BL$
	has the form 	
	$$
	\spLie(n)= \BS^{n} \otimes \Sigma^{-1} \BL(n),
	$$
	whose homology is exactly $\Lie(n)$ concentrated in degree $0$.
	Moreover, the homology of the spectral Lie operad $H_{*}\spLie$ is the Lie operad $\Lie$ in graded abelian groups.
	On the other hand, $\spLie$ is the Goodwillie derivative of the functor $\Omega\Sigma$ on $\Space_*$, see \cite[Section 8]{GoodwillieIII}.
	Moreover, one can check the associated Schur functor $F_{\spLie}$ of $F_{\spLie}$ is indeed given by $\Omega\BL \Sigma$,
	\begin{align*}
		F_{\spLie}(X) &\simeq \coprod_{n\geq 1}
		\big(
		\BS^{n} \otimes \Sigma^{-1}\BL(n) 
		\otimes X^{\otimes n}
		\big)_{h\Sigma_n}\\
		& \simeq 
		\Sigma^{-1}
		\coprod_{n\geq 1}
		\big(
		\BL(n) 
		\otimes (\Sigma X)^{\otimes n}
		\big)_{h\Sigma_n}\\
		& \simeq 
		\Omega F_{\BL}\Sigma(X).
	\end{align*}	
\end{remark}



\section{Induced Monads and Comonads}
\label{Section: Induced Monads}
% Since neither the spectral Lie operad $\spLie$ nor the shifted spectral Lie operad $\BL$ is an operad in $\Sp^{\geq r}$ or $\Sp^{\geq r}_{\tame}$, we need to make additional work to let them act on $\Sp^{\geq r}$ and $\Sp^{\geq r}_{\tame}$.
The goal for this section is to explain how to produce monads on $\Sp^{\geq r}$ and $\Sp^{\geq r}_{\tame}$ from certain monads on $\Sp$.

We start by proving a general fact regarding how localizations interact with endofunctors.
Suppose $L:\CC \to \CD$ is a symmetric monoidal localization
and we let $j:\CD \to \CC$ denote the embedding that is right adjoint to $L$.
We then have an adjunction on the $\infty$-category of endofunctors.
\begin{proposition}
\label{Prop A.4.2}
There is an adjunction
\begin{equation}
\label{A4.2 adjunction}
    \adj{j^*L_*}{\Fun(\CC, \CC)}{\Fun(\CD, \CD)}{j_* L^*}.
\end{equation}
    Moreover, the left adjoint $j^*L_*$ is a localization functor.
\end{proposition}
\begin{proof}
    We need to show there are two pairs of adjunctions
    $$
    \adj{L_{*}}{\Fun(\CC, \CC)}{\Fun(\CC, \CD)}{j_*}
    $$
    and
    $$
    \adj{j^{*}}{\Fun(\CC, \CD)}{\Fun(\CD, \CD)}{L^*}.
    $$
    We only prove the first adjunction as the proof of the second is similar.
    Let $\eta: \id_{\CC} \to j\circ L$ be the unit natural transformation arising from the localization.
    By post-composition, $\eta$ lifts to a natural transformation
    $$
    \eta': \id_{\Fun(\CC,\CC)} \to j_*L_*. 
    $$
    It suffices to check the following composite is an equivalence 
    $$
    \map_{\Fun(\CC,\CD)}(L_{*}F, G) \to 
    \map_{\Fun(\CC,\CC)}(j_*L_{*}F,  j_*G)
    \xrightarrow{\eta^*}
    \map_{\Fun(\CC,\CC)}(F, j_{*}G)
    $$
    for $F\in \Fun(\CC,\CC)$ and $G\in \Fun(\CC, \CD)$.
    But this follows from the composite
    $$
    \map_{\CC}(LF(X), G(X)) \to 
    \map_{\CD}(jLF(X),  jG(X))
    \xrightarrow{\eta^*}
    \map_{\CD}(F(X), jG(X))
    $$
    is an equivalence for every $X\in \CC$.
    
    Note that the counit of the adjunction in (\ref{A4.2 adjunction})
    $$
    j^*L* j_* L^* \to \id_{\Fun(\CD, \CD)}
    $$
    is an equivalence, hence the right adjoint $j_*L^*$ is fully faithful and the proposition is proved.
\end{proof}

The following corollary is a direct consequence of the proposition above and \cite[Proposition 2.2.1.1.]{HA}.
\begin{corollary}
\label{j_*L^* is monoidal}
The functor $j_*L^*: \Fun(\CD,\CD) \to \Fun(\CC,\CC)$ is monoidal.
Therefore, the left adjoint $j^*L_*$ is oplax monoidal.
\end{corollary}

Let $\Fun_L(\CC,\CC)$ be the full subcategory of $\Fun(\CC,\CC)$ spanned by functors that preserve $L$-equivalences. 
The goal of the rest of this section is to show $j^*L_*$ is monoidal when restricted to $\Fun_L(\CC,\CC)$.
Note first that for any $F\in \Fun_L(\CC,\CC)$, we have a natural equivalence
\begin{equation}
\label{LF = LFL}
	L\circ F \simeq L\circ F\circ L
\end{equation}
since $F$ preserves $L$-equivalences.
\begin{remark}
Let $\Fun_L(\CD,\CD)$ denote the essential image of $\Fun_L(\CC,\CC)$ under the functor $j^*L_*$.
For any pair of functors $F,G\in \Fun_L(\CC,\CC)$, there is an natural equivalence
$$
L\circ (F\circ G) \simeq L\circ (F\circ L G)
$$ 
by (\ref{LF = LFL}).
If $f:X\to Y$ is a $L$-equivalence in $\CC$, then
$FG(X) \to FG(Y) \to F\circ LG(Y)$ is a $L$-equivalence since both $F$ and $G$ preserve $L$-equivalences.
Hence, we conclude that both $\Fun_L(\CC,\CC)$ and $\Fun_L(\CD,\CD)$ are closed under composition.
\end{remark}

For $F\in \Fun_{L}(\CC,\CC)$, the right adjoint $j_*L^*$ sends any functor of the form $j^*L_*F$ to a functor in $\Fun_L(\CC,\CC)$; indeed, this follows from the following equivalence
$$
j_*L^*j^*L_* F \simeq j_*L_*F
$$
by (\ref{LF = LFL}).
Since the functor $j_*L_*F$ clearly preserves $L$-equivalences, the functor $j^*L_*$ restricts to a localization
$$
\Fun_L(\CC,\CC) 
	\to 
	\Fun_L(\CD,\CD).
$$
\begin{lemma}
\label{j^*L_* is monoidal when restricted to Fun_L}
	The functor
	$$
	j^*L_*:\Fun_L(\CC,\CC) 
	\to 
	\Fun_L(\CD,\CD)
	$$
	is a monoidal.
\end{lemma}
\begin{proof}
By \cite[Proposition 2.2.1.9.]{HA}, it suffices to check the monoidal structure is compatible with the localization functor $j^*L_*$ in the sense of \cite[Definition 2.2.1.6.]{HA};
	Suppose there is a natural transformation 
$$
T: F \to F'
$$
that is an equivalence after applying $j^*L_*$. 
It suffices to check
$$
j^*L_*(T\circ \id):
L(F\circ G) \to 
L(F'\circ G)
$$ 
is an equivalence for any $G\in \Fun_L(\CC,\CC) $.
Consider the commutative diagram
\[
\begin{tikzcd}
L(F\circ G) & LF \circ j\circ LG\\
L(F'\circ G) & LF' \circ j\circ LG.
    \arrow[from=1-1, to=1-2]
	\arrow[from=1-1, to=2-1]
	\arrow[from=2-1, to=2-2]
	\arrow[from=1-2, to=2-2]
\end{tikzcd}
\]
The horizontal arrows are equivalences since both $F$ and $F'$ preserve $L$-equivalences, and the right vertical arrow is an equivalence followed from the assumption.
Therefore, the left arrow is an equivalence and the proof is now complete.
\end{proof}
\begin{remark}
\label{j^*L_* is monoidal on Fun_L}
As a consequence, if $F\in \Fun_{L}(\CC,\CC)$ is a monad, then 
$j^*L_*(F)$ is a monad on $\CD$. For simplicity, we will abuse notation by writing $LF$ for the monad $j^*L_*(F)$.
\end{remark}

Let $\{\CO(k)\}_{k \geq 1}$ be a symmetric sequence in $\Sp$ such that the connectivity of $\CO(k)$ is $1-k$ for each $k$. 
For $r \geq 1$, let $X$ be an $r$-connective spectrum.
 Since $(\CO(k) \otimes X^{\otimes k})_{h\Sigma_k}$ is still $r$-connective, the Schur functor associated to $\CO$ 
    $$
    F_{\CO}(X) \simeq 
    \coprod_{k \geq 1} (\CO(k) \otimes X^{\otimes k})_{h\Sigma_k}
    $$
induces an endofunctor on the $\infty$-category $\Sp^{\geq r}$ of $r$-connective spectra.

Let $\SSeq(\Sp)^{\geq 1}$ be the full subcategory of $\SSeq(\Sp)$ spanned by symmetric sequences $\{\CO(k)\}_{k \geq 1}$ such that $\CO(k)$ is $(1-k)$-connective.
\begin{lemma}
\label{1-connective operad is closed under composition product}
	The $\infty$-category $\SSeq(\Sp)^{\geq 1}$ is closed under the composition product.
\end{lemma}
\begin{proof}
	For any $\CO,\CP \in \SSeq(\Sp)^{\geq 1}$, it suffices to check $(\CO \circ \CP)(n)$ is still $(1-n)$-connective for every $n\geq 1$.
	By the formula in Remark \ref{formula for composition product}, a component in $(\CO \circ \CP)(n)$ is of the form
	$$
	\CO(k) \otimes \CP(n_1) \otimes \cdots \otimes \CP(n_k)
	$$
	where $\sum_i n_i = n$. The lemma then follows from the calculation of the connectivity of 
	$	\CO(k) \otimes \CP(n_1) \otimes \cdots \otimes \CP(n_k)$, which equals to 
	$$
	1- k + \sum_i (1-n_i)= 1 - \sum_in_i=1-n.
	$$
\end{proof}

We extend the definition of coanlytic functors in \cite[Definition 4.3]{heuts2018lie}.
\begin{definition}
\label{coanalytic functors on r-conn spectra}
We say an endofunctor $F:\Sp^{\geq r} \to \Sp^{\geq r}$ is \emph{coanalytic} over $\Sp$ if there is a natural equivalence
	$$
	F(X) \simeq
	\coprod_{k\geq 1} (\CO(k)\otimes X^{\otimes k})_{h\Sigma_k}
	$$
	for $\{\CO(k)\}_{k \geq 1}$ a symmetric sequence in $\SSeq(\Sp)^{\geq 1}$. 
	We write $\coAn_{\Sp}(\Sp^{\geq r})$ for the full sbucategory of $\Fun(\Sp^{\geq r},\Sp^{\geq r})$ spanned by coanalytic functors over $\Sp$.
\end{definition}
As a consequence of Lemma \ref{1-connective operad is closed under composition product}, the composition of two coanalytic functors is again a coanalytic functor, hence the monoidal structure on $\Fun(\Sp^{\geq r}, \Sp^{\geq r})$ restricts to one on $\coAn_{\Sp}(\Sp^{\geq r})$.
Moreover, if $\CO$ is an operad (resp. cooperad) in $\SSeq(\Sp)^{\geq 1}$, then $F_{\CO}$ restricts to a monad (resp. comonad) on $\Sp^{\geq r}$.

\begin{example}
	The shifted free Lie algebra monad $F_{\BL}$ is a coanalytic functor on $\Sp^{\geq r}$ over $\Sp$, since $\BL(n)$ is a wedge of $\BS^{1-n}$.
	Similarly, $F_{\spLie}$ is a coanalytic functor on $\Sp^{\geq r}$.
\end{example}

\begin{example}
    The free commutative comonad $F_{\Com}$ is a coanalytic functor
    $\Sp^{\geq r}$ over $\Sp$, since $\Com(n)$ is $\BS$.
\end{example}

\begin{remark}
\label{coanalytic functors preserve tame equivalences}
	Since tame equivalences are closed under tensor products and colimits,
	we conclude that coanalytic functors on $\Sp^{\geq r}$ over $\Sp$ preserve tame equivalences. 
\end{remark}
Combining Lemma \ref{j^*L_* is monoidal when restricted to Fun_L} and Remark \ref{coanalytic functors preserve tame equivalences}, we end this section with the following proposition.
\begin{proposition}
\label{Induced Monads}
If $\CO$ (resp. $\CQ$) be an $\infty$-operad (resp. $\infty$-cooperad) whose underlying symmetric sequence is in $\SSeq(\Sp)^{\geq 1}$.
Then we obtain an induced monad $L_{\tame} F_{\CO}$ (resp. comonad $L_{\tame} F_{\CQ}$) on the $\infty$-category $\Sp^{\geq r}_{\tame}$ of tame spectra.
\end{proposition}

\section{Commutative Coalgebras in Tame Spectra}
\label{Commutative coalgebras in tame spectra}

In this section, we define and study the $\infty$-category of commutative coalgebras in the category of $r$-tame spectra. 
The main aim is to show the $\infty$-category of divided power, conilpotent commutative coalgebras is equivalent to the $\infty$-category of commutative coalgebras in $\Sp^{\geq r}_{\tame}$.
We start by collecting some results from \cite{LurieEllipticI}.

\begin{definition}
    Let $\mathcal{C}$ be a symmetric monoidal $\infty$-category. The $\infty$-category $\coCAlg(\CC)$ of commutative coalgebras in $\CC$ is defined to be
    $
    \coCAlg(\CC):= \CAlg(\CC^{op})^{op}.
    $
\end{definition}



\begin{proposition}
\label{Cor 3.1.5. Ellip}
\cite[Corollary 3.1.5]{LurieEllipticI}
	Let $\mathcal{C}$ be a symmetric monoidal $\infty$-category. Suppose that the $\infty$-category $\mathcal{C}$ is presentable and that the tensor product functor $\otimes: \mathcal{C} \times \mathcal{C} \rightarrow \mathcal{C}$ preserves colimits separately in each variable. Then the forgetful functor $\coCAlg(\mathcal{C}) \rightarrow \mathcal{C}$ admits a right adjoint $\cofree: \mathcal{C} \rightarrow \coCAlg(\mathcal{C})$.
\end{proposition}


\begin{corollary}
The forgetful functor 
$$
\oblv_{\coCAlg}:\coCAlg(\Sp_{\tame}^{\geq r})\to \Sp^{\geq r}_{\tame}
$$ admits a right adjoint functor, which we will denote by $\cofree_{\tame}$.
\end{corollary}
\begin{proof}
	 Note that $\Sp^{\geq r}_{\tame}$ is presentable as it's a localization of the presentable $\infty$-category $\Sp^{\geq r}$. 
	 Since the tensor product $\hat{\otimes}$ in $\Sp_{\tame}^{\geq r}$ preserves colimits separately in each variable by Remark \ref{symmetric monoidal structure on tame spectra}, the existence of the cofree commutative coalgebra functor is ensured by Proposition \ref{Cor 3.1.5. Ellip}.
\end{proof}

Since the monad $F_{\Com}$ associated to the commutative operad has underlying endofunctor
$$
F_{\Com}(X) := \coprod_{n\geq 1} (X^{\otimes n})_{h\Sigma_n},
$$ hence $F(X):= \prod_{n\geq 1} (X^{\otimes n})^{h\Sigma_n}$ defines a comonad on $\CC$.
For a general symmetric monoidal $\infty$-category $\CC$, we do not know any explicit identification of the cofree comonad $Q:=\oblv_{\coCAlg}\circ \cofree$. 
However, we do know an explicit formula for the comonad $Q_{\tame}:=\oblv_{\coCAlg}\circ \cofree_{\tame}$ in the $\infty$-category of tame spectra. 
To explain this, we need the following lemma which can be deduced from \cite[Proposition 3.1.3.3]{HA} and \cite[Example 3.1.1.17]{HA}.
\begin{lemma}
\label{Cofree commutative coalgebra}
Let $\CC$ be a presentable symmetric monoidal $\infty$-category.
Define $F$ to be the endofunctor on $\CC$
$$
F(X):= \prod_{n\geq 1} (X^{\otimes n})^{h\Sigma_n}.
$$
If the canonical map 
$$
\gamma: \big( \prod_{n\geq 1} (X^{\otimes n})^{h\Sigma_n} \big) \otimes Y \to 
\prod_{n\geq 1} (X^{\otimes n} \otimes Y)^{h\Sigma_n}
$$
is an equivalence for any $Y\in \CC$ with trivial $\Sigma_n$-action, for all $n$,
then the cofree comonad $Q$ is given by $F$.
\end{lemma}
\begin{proof}
    By \cite[Definition 3.1.3.1.]{HA} the cofree coalgebra of an obejct $X$ in $\CC$ is defined as a operadic limit diagram (cf. \cite[Definition 3.1.1.2.]{HA}) $p:\Fin_{*} \to \CC$.
    By a dual statement of \cite[Proposition 3.1.3.3]{HA} in the special case where $\CA$ is the trivial $\infty$-operad, $\CB$ and $\CO$ are the commutative $\infty$-operad $\Fin_{*}$, such a operadic limit exists.
    The lemma then follows from the dual version of \cite[Example 3.1.1.17]{HA}, which says that a diagram $p:\Fin_{*} \to \CC$ is an operadic limit diagram if it remains as a limit diagram in $\CC$ after tensoring with any object $Y\in\CC$. 
    In our case, this means that $\prod_{n\geq 1} (X^{\otimes n})^{h\Sigma_n}$ is an operadic limit diagram if 
    $\big( \prod_{n\geq 1} (X^{\otimes n})^{h\Sigma_n} \big) \otimes Y$ is a limit diagram for any $Y\in \CC$, which is the condition required for $\gamma$ being an equivalence.
    
\end{proof}

We now prove that the $\infty$-category of tame spectra satisfies the conditions of Lemma
\ref{Cofree commutative coalgebra}, therefore we obtain a simple description of the comonad $Q_{\tame}$.
We write $\Sym_{\tame}$ for the symmetric algebra functor on $\Sp^{\geq r}_{\tame}$, which is given explicitly by
$$
\Sym_{\tame}(X) :=\bigoplus_{n\geq 1} L_{\tame}(X^{\otimes n})_{h\Sigma_n} .
$$
\begin{proposition}
\label{Cofreee commutative comonad}
	The cofree commutative comonad on the $\infty$-category $\Sp^{\geq r}_{\tame}$ of tame spectra is given by
	 $$
	 Q_{\tame}(X) \simeq \bigoplus_{n\geq 1} L_{\tame}(X^{\otimes n})_{h\Sigma_n}
	 \simeq
	 \Sym_{\tame}(X)
	 $$
	 for any $X \in \Sp^{\geq r}_{\tame}$.
\end{proposition}
\begin{proof}
    We first claim that the canonical map 
    $$
	\gamma: \bigoplus_{n\geq 1} (L_{\tame}X^{\otimes n})_{h\Sigma_n}
	\to 
	\prod_{n\geq 1} (L_{\tame}X^{\otimes n})^{h\Sigma_n}
	$$
	is an equivalence for any $X \in \Sp^{\geq r}_{\tame}$.
% 	Since both the $\infty$-categories $\coCAlg^{\divpow,\nil}(\Sp^{\geq r}_{\tame})$ and $\coCAlg(\Sp^{\geq r}_{\tame})$ are comonadic over $\Sp^{\geq r}_{\tame}$, it suffices to check their correspoding comonads are equivalent.
% 	$$
% 	\adj{U}{\coCAlg^{\nil}(\Sp^{\geq r}_{\tame})}{\Sp^{\geq r}_{\tame}}{\cofree^{\nil}}
% 	$$
% 	agrees with the comonad $F_{\Com}$. Indeed, we have a natural map
    Note that the target is equivalent to 
    $$
    \prod_{n\geq 1} (L_{\tame} X^{\otimes n})_{h\Sigma_n},
    $$
    by Proposition \ref{Tate vanishing for tame spectra}.
    
    We now show that $\gamma$ is an equivalence after applying $k$-truncation functor $\tau_{\leq k}$ for each integer $k\geq r$.
	There exists a maximum integer $l(k)$ such that $X^{\otimes (l+1)}$ is $(k+1)$-connective.
	Hence the $k$-truncation of $\gamma$ can be identified as a map
	$$
	\tau_{\leq k} \gamma: \bigoplus_{n\geq 1}^{l(k)}
	\tau_{\leq k} (L_{\tame}X^{\otimes n})_{h\Sigma_n}
	\to 
	\bigoplus_{n\geq 1}^{l(k)}
	\tau_{\leq k} (L_{\tame}X^{\otimes n})_{h\Sigma_n}
	$$
	 which is an equivalence for every $k$. Hence, $\gamma$ is an equivalence.
	 Since tensor product commutes with colimits in $\Sp^{\geq r}_{\tame}$, $F(X):=\prod_{n\geq 1} (L_{\tame} X^{\otimes n})^{h\Sigma_n}$ satisfies the condition of Lemma
    \ref{Cofree commutative coalgebra}, and thus the comonad $Q_{\tame}$ is given by 
    $$
    Q_{\tame}(X) \simeq  \Sym_{\tame}(X).
    $$
	\end{proof}
We now define the $\infty$-category of divided power, conilpotent coalgebras in $\Sp_{\tame}^{\geq r}$. Note that $\Sp_{\tame}^{\geq r}$ is a non-unital symmetric monoidal $\infty$-category, so there is no commutative cooperad in $\Sp_{\tame}^{\geq r}$. However, we can define a comonad which comes from the commutative cooperad in $\Sp$ via tame localization.

By example \ref{Symmetric algebra}, the Schur functor $F_{\Com}$ associated to the commutative cooperad in $\Sp$ is a comonad and is given by
$$
F_{\Com}(X) := \coprod_{n\geq 1} (X^{\otimes n})_{h\Sigma_n}.
$$
Note that $F_{\Com}$ restricts to a comonad on the $\infty$-category $\Sp^{\geq r}$ of $r$-connective spectra, since colimits in $\Sp^{\geq r}$ are computed in $\Sp$.
By Proposition \ref{Induced Monads}, we obtain a comonad $L_{\tame}F_{\Com}$ on $\Sp_{\tame}^{\geq r}$, given by 
$$
L_{\tame} F_{\Com}(X) := \coprod_{n\geq 1} L_{\tame}(X^{\otimes n})_{h\Sigma_n}.
$$
as $L_{\tame}$ is colimit-preserving and symmetric monoidal.


\begin{definition}
\label{Def of tame dp, nil coalgebras}
    The $\infty$-category of \emph{divided power, conilpotent coalgebras in tame spectra} is defined to be the $\infty$-category of left comodules over the comonad $L_{\tame}F_{\Com}$
    \[
    \coCAlg^{\divpow, \nil}(\Sp_{\tame}^{\geq r}):= \operatorname{LcoMod}_{L_{\tame}F_{\Com}}(\Sp_{\tame}^{\geq r}).
    \]
\end{definition}
We now want to show these two $\infty$-categories of coalgebras in tame spectra are actually equivalent. 
Since the underlying endofunctors of $Q_{\tame}$ and $L_{\tame}F_{\Com}$ are equivalent, it suffices to show there is a natural transformation of comonads
$$
\Gamma: L_{\tame}F_{\Com}\to 
Q_{\tame},
$$
which gives rise to an equivalence $L_{\tame}F_{\Com}\simeq Q_{\tame}$.
By the discussion in Appendix \ref{Construction of the Comparison Functor}, there is a map of comonads on $\Sp^{\geq r}_{\tame}$
$$
\Gamma: (L_{\tame})_{*} j^{*} F_{\Com} \to Q_{\tame}.
$$
which is the unique map that makes the diagram in Remark \ref{F_Com to Q_C} commute.
The map of comonads $\Gamma$ then induces a comparison functor 
$$
\zeta:\coCAlg^{\divpow,\nil}(\Sp^{\geq r}_{\tame}) \to
\coCAlg(\Sp^{\geq r}_{\tame}).
$$
The following proposition now follows immediately from Proposition \ref{Cofreee commutative comonad}.
\begin{proposition}
\label{all coalgebras are equivalent}
	The comparison functor $\zeta$ is an equivalence of $\infty$-categories.
\end{proposition}
\begin{proof}
Since the forgetful functor $\Comonad(\Sp^{\geq r}_{\tame}) \to \End(\Sp^{\geq r}_{\tame})$ is conservative,
it suffices to show the $\Gamma$ induces an equivalence between the underlying endofunctors of $L_{\tame}F_{\Com}$ and $Q_{\tame}$. For $X\in \Sp^{\geq r}_{\tame}$, the map $\Gamma$ is obtained from the projection $L_{\tame}F_{\Com}X \to X$ to the first factor (see Appendix \ref{Construction of the Comparison Functor}), which agrees with the canonical projection $Q_{\tame}X\to X$ by \ref{Cofreee commutative comonad}. Hence $\Gamma$ is an equivalence since it is an equivalence between the underlying endorfunctors.

\end{proof}




%Combining the two adjunctions, we obtain a diagram:
%\[
%\begin{tikzcd}
%\CC \arrow[r,shift left=1,"\free_{\CO}"]  & \Alg_{\CO}(\CC) \arrow[r,shift left=1,"\TAQ_{\CO}"] \arrow[l,shift left=1,"\oblv_{\CO}"]  & \CC \arrow[l,shift left=1,"\trivial_{\CO}"] 
%\end{tikzcd}
%\]
%where left adjoints are on top and both composites are equivalent to $id_{\CC}$.
%% Denote $F_{\CO}:\CC\rightarrow \CC$ its associated monad.
%\subsection{Conilpotent coalgebras over a cooperad}
%Let $\CP$ be a connected cooperad.
%Let $F_{\CP}$ be the comonad associated to $\CP$. We denote the category of coalgebras over $F_{\CP}$ by $\coAlg^{nil,dp}_{\CP}(\CC)$. An object $X\in \coAlg^{nil,dp}_{\CP}(\CC)$ is equipped with a structure map:
%$$
%X\rightarrow \bigoplus_{n\geq 1}\big( \CP(n)\otimes X^{\otimes n}\big)_{h\Sigma_n}.
%$$
%We will refer to $\coAlg^{nil,dp}_{\CP}(\CC)$ \textit{the category of conilpotent divided power $\CP$-coalgebras}. 
%Dual to the algebra case, we have a diagram of two pair of adjoint functors:
%\[
%\begin{tikzcd}
%\CC \arrow[r,shift left=1,"\cofree^{nil,dp}_{\CP}"]  & \coAlg^{nil,dp}_{\CP}(\CC) \arrow[r,shift left=1,"\Prim^{nil,dp}_{\CP}"] \arrow[l,shift left=1,"\oblv^{nil,dp}_{\CP}"]  & \CC \arrow[l,shift left=1,"\trivial^{nil,dp}_{\CP}"] 
%\end{tikzcd}
%\]
%where functors at the bottom are left adjoints and both composites are equivalent to $id_\CC$.
%The adjective conilpotent stands for the direct sum and the adjective divided power corresponds to coinvariants in $F_{\CP}$.
%
%
%
%\begin{theorem}[\cite{Francis-Gaitsgory}, \cite{HeutsSurvey}]
%The functor $\TAQ_{\CO}$ factors as 
%$$
%\Alg_{\CO}(\CC) \xrightarrow{B_\CO} \coAlg^{nil,dp}_{\Barconstruction(\CO)}(\CC)\xrightarrow{\oblv_{\Barconstruction (\CO)}} \CC.
%$$	
%
%\end{theorem}


\section{Lie Algebras in Tame Spectra}
\label{Lie Algebras in Tame Spectra}
In this section, we discuss spectral Lie algebras in $\Sp$ and $\Sp^{\geq r}_{\operatorname{tame}}$. We will prove that the $\infty$-category of tame spectral Lie algebras can be identified as the full subcategory of spectral Lie algebras whose underlying spectra are tame.
We then define the Chevalley-Eilenberg functor that goes from the $\infty$-category of spectral Lie algebras to the $\infty$-category of divided power, conilpotent commutative coalgebras.


% Using the theory of Koszul duality introduced in the previous section, we will state the main result of \cite{Ching-Harper} and apply to the tame spectra case. The main result is that the $\infty$-category $\Alg_{\Lie}(\Sp_{tame})$ of tame spectral Lie algebras is equivalent to the $\infty$-category $\coAlg^{nil, dp}_{\Com}(\Sp_{tame})$ of conilpotent divided power coalgebras.
\begin{definition}
\label{Spectral Lie operad}
We define the $\infty$-category $\Alg_{\spLie}(\Sp)$ of \emph{spectral Lie algebras} to be the $\infty$-category of algebras over the spectral Lie operad $\spLie$.
\end{definition}

\begin{remark}
Note that our definition of spectral Lie algebras might be different from the one given in the literature, e.g. \cite{Camarena_mod2_free_spectral_Lie_algebra} and \cite{ChingBar}, where $\BL$ is referred as the spectral Lie operad. 
Our definition of the spectral Lie operad $\spLie$ differs by a shift.
The advantage of this definition is that the homology $H_{*}\spLie$ is precisely the Lie operad in abelian groups, hence the homology of a spectral Lie algebra is a graded Lie algebra.
\end{remark}

By Proposition \ref{Induced Monads}, $L_{\tame}F_{\spLie}$ defines a monad on $\Sp^{\geq r}_{\tame}$.
The underlying endofunctor of the monad $L_{\tame}F_{\spLie}$ on $\Sp^{\geq r}_{\tame}$ is simply given by the tame localization of the free spectral Lie algebra monad on $\Sp^{\geq r}$:
\begin{align*}
X \mapsto  
\coprod_{n\geq 1}
		L_{\tame}\big(
		 \spLie(n) \otimes (L_{\tame} X)^{\otimes n}
		\big)_{h\Sigma_n}.
\end{align*}


We are now ready to define the $\infty$-category of tame spectral Lie algebras.
\begin{definition}
\label{Def of tame spectral Lie algebras}
    We define the $\infty$-category $\Alg_{\spLie}(\Sp^{\geq r}_{\tame})$ of \emph{tame spectral Lie algebras} to be 
    $$
    \Alg_{\spLie}(\Sp^{\geq r}_{\tame}) := \LMod_{	L_{\tame}F_{\spLie}}(\Sp^{\geq r}_{\tame}).
    $$
    Similarly, we define the $\infty$-category of \emph{shifted tame spectral Lie algebras}
    $$
    \Alg_{\BL}(\Sp^{\geq r}_{\tame}) := \LMod_{	L_{\tame}F_{\BL}}(\Sp^{\geq r}_{\tame}).
    $$
\end{definition}

On the level of underlying spectra,
the induced functor 
$$
\Alg_{\spLie}(\Sp)^{\geq r} 
\to 
\Alg_{\spLie}(\Sp^{\geq r}_{\tame}).
$$
is simply given by sending an $r$-connective spectrum $X$ to its tame localization $L_{\tame}X$.

\begin{remark}
Although the monad $L_{\tame}F_{\Lie}$ does not come from an operad in $\Sp^{\geq r}_{\tame}$, it does have all the associated functors we discussed in Section \ref{Coalgebras over cooperads and Koszul Duality}.
Indeed, the spectral Lie monad on $\Sp^{\geq r}$ has unit $\eta$ and augmentation $\epsilon$ natural transformations so that the composition 
\[
\id_{\Sp^{\geq r}}
\xrightarrow{\eta}
F_{\Lie}\xrightarrow{\epsilon}
\id_{\Sp^{\geq r}}
\]
is the identity natural transformation.
Applying tame localization, there is again a composite of monads on $\Sp^{\geq r}_{\tame}$
\[
\id_{\Sp^{\geq r}_{\tame}}
\xrightarrow{\eta}
L_{\tame}F_{\Lie}\xrightarrow{\epsilon}
\id_{\Sp^{\geq r}_{\tame}}
\]
which is equivalent to the identity natural transformation on $\Sp^{\geq r}_{\tame}$.
Therefore, we have the adjoint pairs between tame spectral Lie algebras and tame spectra
\[
\begin{tikzcd}
	%%%% The nodes %%%%%%%%%
\Sp^{\geq r}_{\tame} & \Alg_{\spLie}(\Sp^{\geq r}_{\tame}) & \Sp^{\geq r}_{\tame}
%%%% Now the arrows %%%%
	\arrow[from=1-1, to= 1-2, shift left = 1, "\Free_{\spLie}" above]
	\arrow[from=1-2, to=1-1, shift left = 1, "\oblv{\spLie}" below]
	\arrow[from=1-2, to= 1-3, shift left = 1, "\cot_{\spLie}" above]
	\arrow[from=1-3, to=1-2, shift left = 1, "\trivial_{\spLie}" below].
\end{tikzcd}
\]
\end{remark}

\begin{remark}
Dually, recall we have defined the $\infty$-category of divided power, conilpotent tame commutative coalgebras in Definition \ref{Def of tame dp, nil coalgebras}. 
As in the case of spectral Lie algebras, we have a pair of adjunctions
\[
\begin{tikzcd}
%%%% The nodes %%%%%%%%%
\Sp^{\geq r}_{\tame} & \coAlg^{\divpow, \nil}_{\Com}(\Sp^{\geq r}_{\tame}) & \Sp^{\geq r}_{\tame}.
%%%% Now the arrows %%%%
	\arrow[from=1-1, to= 1-2, shift left = 1, "\cofree^{\nil}_{\Com}" above]
	\arrow[from=1-2, to=1-1, shift left = 1, "\oblv^{\nil}_{\Com}" below]
	\arrow[from=1-2, to= 1-3, shift left = 1, "\operatorname{Prim}^{\nil}_{\Com}" above]
	\arrow[from=1-3, to=1-2, shift left = 1, "\trivial^{\nil}_{\Com}" below]
\end{tikzcd}
\]
\end{remark}





We claim the $\infty$-category of tame spectral Lie algebras is a full subcategory of the $\infty$-category of $r$-connective spectral Lie algebras whose underlying spectra are tame. It turns out that this is a consequence of the following more general result.
\begin{proposition}
\label{Lifting localization to algebra category}
Let $\CC$ and $\CD$ be symmetric monoidal $\infty$-categories whose tensor products are compatible with colimits.
Suppose $L:\CC \to \CD$ is a symmetric monoidal localization functor.
If $F_\CO$ is a monad in $\CC$, then the induced functor
$$
L' : \Alg_{F_\CO}(\CC) \to \Alg_{LF_\CO}(\CD).
$$
is a localization.
\end{proposition}
\begin{proof}
	The existence of the functor $L'$ follows from Remark \ref{j^*L_* is monoidal on Fun_L}. It remains to show $L'$ is a localization functor. Let $g$ be the fully faithful right adjoint of $L$. We first claim that $g$ lifts to a functor 
	$$
	g': \Alg_{LF_\CO}(\CD)
	\to 
	\Alg_{F_\CO}(\CC),
	$$
	which is right adjoint to $L'$. 
	Indeed, since $L$ is symmetric monoidal, it follows that $g$ is lax symmetric monoidal; hence $g$ induces a functor $g': \Alg_{LF_\CO}(\CD)
	\to 
	\Alg_{F_\CO}(\CC)$.
	To see that $g'$ is right adjoint to $L'$, let $\eta: id_{\CC} \to gL$ be the unit natural transformation.
	Note that $\eta$ is a $\End(\CC)$-linear natural transformation in the sense of \cite[Definition 4.6.2.7.]{HA}, hence it induces a natural transformation $\eta': \id_{\Alg_{F_{\CO}}(\CC)} \to g'\circ L'$.
	We claim the map
	$$
	\rho:
	\map_{\Alg_{LF_\CO}(\CD)}(L'M, N)
	\to 
	\map_{\Alg_{F_\CO}(\CC)}(M, g'N),
	$$
	induced from $\eta'$,
	is an equivalence for any $M\in \Alg_{F_\CO}(\CC)$ and $N\in \Alg_{LF_\CO}(\CD)$. 
	
	First observe that $L'$ sends free $F_\CO$-algebras to free $LF_{\CO}$-algebras, i.e.
	$$
	L'(\Free_{F_{\CO}} X)\simeq \Free_{LF_{\CO}} f(X)
	$$
	for $X\in \CC$,
	as $L$ is symmetric monoidal and colimit-preserving. 
	Hence, 
    \begin{align*}
        \map_{\Alg_{LF_{\CO}}(\CD)}(L'\Free_{F_{\CO}} X, N) & \simeq \map_{\Alg_{LF_{\CO}}(\CD)}(\Free_{LF_{\CO}} L(X), N)\\
        & \simeq \map_{\CD}(L(X), \oblv_{LF_{\CO}}N)\\
        & \simeq \map_{\CC}(X, g \circ \oblv_{LF_{\CO}}N)\\
        & \simeq \map_{\CC}(X, \oblv_{F_{\CO}}\circ g' N)\\
        & \simeq \map_{\CC}(\Free_{F_{\CO}}  X, g' N)
    \end{align*}	
    and we conclude that
	$\rho$ is an equivalence whenever $M$ is a free $F_{\CO}$-algebra. For a general $F_{\CO}$-algebra, we use Proposition \ref{free resolutino of O-algebras} to write $M$ as a geometric realization of a $\oblv_{F_{\CO}}$-split simplicial free $F_{\CO}$-algebras. Then the claim follows from the Barr-Beck-Lurie theorem \cite[Theorem 4.7.3.5.]{HA} and the fact that $L'$ preserves geometric realizations of $\oblv_{F_{\CO}}$-split simplicial objects.
	
    For the fully-faithfulness of $g'$, it suffices to show the counit map 
    $L'g'N \to N$ is an equivalence for any $N\in \Alg_{LF_{\CO}}(\CD)$. This follows from the fact that the forgetful functor $\oblv_{LF_{\CO}}$ is conservative and $g$ is fully faithful.
\end{proof}

\begin{corollary}
\label{Identification of tame Lie algebras}
	The $\infty$-category $\Alg_{\spLie}(\Sp^{\geq r}_{\tame})$ can be identified with the full subcategory of $\Alg_{\spLie}(\Sp)^{\geq r}$ spanned by spectral Lie algebras whose underlying spectra are tame.
\end{corollary}
\begin{proof}
    Proposition \ref{Lifting localization to algebra category} provides a localization functor
	$$
	L': \Alg_{\spLie}(\Sp)^{\geq r} \to \Alg_{\spLie}(\Sp^{\geq r}_{\tame}).
	$$
	The corollary then follows from the commuting diagram
\[
\begin{tikzcd}
	\Alg_{\spLie}(\Sp)^{\geq r} & \Alg_{\spLie}(\Sp^{\geq r}_{\tame})\\
	\Sp^{\geq r}  & 
	\Sp^{\geq r}_{\tame}
	\arrow[from=1-2, to= 1-1]
	\arrow[from=1-1, to=2-1, "\oblv" left]
	\arrow[from=1-2, to=2-2, "\oblv'" ]
	\arrow[from=2-2, to= 2-1]
\end{tikzcd}
\]
where the horizontal functors are fully faithful. 

\end{proof}


We now give an algebraic characterization of tame spectral Lie algebras and tame commutative coalgebras.
We first define Lie algebras in $\Mod_{H\BZ}$, for which we need the following result from Haugseng.
\begin{lemma}
\label{induced maps on SSeq}
\cite[Corollary 4.2.9.]{Haugsengsymseq}
Let $\CC$ and $\CD$ be preadditive symmetric monoidal $\infty$-categories whose tensor products are compatible with colimits. Let
$$
f: \CC \to \CD
$$
be a colimit-preserving, symmetric monoidal functor.
Postcomposing with $f$ gives a monoidal functor
$$
\SSeq(\CC) \to 
\SSeq(\CD).
$$
\end{lemma}	
Since the functor 
$(-\otimes H\BZ):\Sp \to \Mod_{H\BZ}$ satisfies the condition of Lemma \ref{induced maps on SSeq}, we conclude that the symmetric sequence
$$
(\spLie\otimes H\BZ)(n) := \spLie(n)\otimes H\BZ
$$ defines an operad in $\Mod_{H\BZ}$.
\begin{definition}
We define the $\infty$-category of Lie algebras in $H\BZ$-modules by 
$$
\Alg_{\spLie}(\Mod_{H\BZ}): = \LMod_{\spLie\otimes H\BZ}(\Mod_{H\BZ}).
$$
\end{definition}

\begin{remark}
The homotopy groups of $\spLie(n)\otimes H\BZ$ are the homology groups of $\spLie(n)$ (concentrated in degree $0$), hence $\pi_* \spLie(n)\otimes H\BZ$ is the Lie operad in graded abelian groups by our discussion in \S \ref{The spectral Lie operad}.
Since $\Mod_{H\BZ}$ models the derived $\infty$-category $D(\BZ)$ of chain complexes, we can identify 
$\Alg_{\spLie}(\Mod_{H\BZ})$ as the $\infty$-category of dg Lie algebras over $\BZ$.
\end{remark}

Let $L_{\tame}$ be the localization $\Mod_{H\BZ}^{\geq r} \to (\Mod_{H\BZ}^{\geq r})_{\tame}$. Since the associated Schur functor for the operad $\spLie\otimes H\BZ$ also preserves tame $H\BZ$-equivalences, by Lemma \ref{j^*L_* is monoidal when restricted to Fun_L}, we obtain a monad $L_{\tame}F_{\spLie \otimes H\BZ}$ on $(\Mod_{H\BZ}^{\geq r})_{\tame}$.

\begin{definition}
We define the $\infty$-category of tame Lie algebras in $(\Mod_{H\BZ}^{\geq r})_{\tame}$ by 
$$
\Alg_{\spLie}((\Mod_{H\BZ}^{\geq r})_{\tame}): = \LMod_{L_{\tame}F_{\spLie \otimes H\BZ}}((\Mod_{H\BZ}^{\geq r})_{\tame}).
$$
\end{definition}
\begin{remark}
\label{Identify tame Lie algebra with Dwyer's Lie algebra}
Since the underlying free Lie monad on $(\Mod_{H\BZ}^{\geq r})_{\tame}$ is given by
$$
L_{\tame}F_{\spLie \otimes H\BZ}(M)
\simeq \coprod_{k\geq 1} 
L_{\tame}(\spLie(n)\otimes H\BZ \underset{\BZ}{\otimes} M^{\underset{\BZ}{\otimes}n})_{h\Sigma_n},
$$
by Proposition \ref{Lifting localization to algebra category}, we conclude that $\Alg_{\spLie}((\Mod_{H\BZ}^{\geq r})_{\tame})$ is the full subcategory of 
$\Alg_{\spLie}(\Mod^{\geq r}_{H\BZ})$ consisting of Lie algebras in $\Mod^{\geq r}_{H\BZ}$ whose underlying spectra are tame.
Therefore, we can identify $\Alg_{\spLie}((\Mod_{H\BZ}^{\geq r})_{\tame})$ as Dwyer's tame Lie algebras in \cite{Dwyer}.
\end{remark}

Recall from Theorem \ref{algebraic description of tame spectra} that we have a symmetric monoidal equivalence
$$
L_{\tame}(-\otimes H\BZ):
\Sp^{\geq r}_{\tame} \simeq
(\Mod_{H\BZ}^{\geq r})_{\tame}.
$$
Apply the discussion above, we obtain the following lemma.
\begin{lemma}
There is an equivalence of $\infty$-categories
$$
\Alg_{\spLie}(\Sp^{\geq r}_{\tame}) \simeq \Alg_{\spLie}\big((\Mod_{H\BZ}^{\geq r})_{\tame}\big).
$$
\end{lemma}
% By the same proof as in Corollary \ref{Identification of tame Lie algebras}, we obtain the following corollaries.

By an argument dual to the proof of Corollary \ref{Identification of tame Lie algebras}, we obtain the analogous result for tame commutative coalgebras in $\Sp^{\geq r}_{\tame}$. 
\begin{corollary}
\label{Identification of tame dp,nil coalgebras}
    The $\infty$-category $\coCAlg(\Sp^{\geq r}_{\tame})$ can be identified with the full subcategory of $\coCAlg^{\divpow, \nil}(\Sp)^{\geq r}$ spanned by commutative divided power, conilpotent coalgebras whose underlying spectra are tame.
\end{corollary}

\begin{remark}
\label{Identification of tame commutative coalgebras in Mod_HZ}
    The $\infty$-category $\coCAlg(\Sp^{\geq r}_{\tame})$ of tame commutative coalgebras can be identified with the full subcategory of $\coCAlg^{\divpow, \nil}(\Mod_{H\BZ})^{\geq r}$ spanned by commutative divided power, conilpotent coalgebras whose underlying $H\BZ$-module spectra are tame.
\end{remark}


To conclude this section,
we discuss Koszul duality between Lie algebras and divided power, conilpotent commutative coalgebras.
That is, we consider the functor
$$\indec_{\CO}: \Alg_{\CO}(\CC)\to \coAlg_{\Barconstruction(\CO)}(\CC)$$
for $\CO$ the Lie operad. 
Classically, if $\CC$ is the $\infty$-category $\Sp_{\BQ}$ of rational spectra, or equivalently, the $\infty$-category of rational chain complexes, then the functor 
$$
\cot_{\BL}: \Alg_{\BL}(\Sp_{\BQ}) 
\to 
\Sp_{\BQ}
$$
computes the Chevalley-Eilenberg cohomology of a dg Lie algebra over $\BQ$. 

\begin{definition}
\label{CChevalley-Eilenberg functor}
  We define two versions of the \emph{Chevalley-Eilenberg} functor on a stable $\infty$-category $\Sp$:
    \begin{itemize}
        \item  
        $
        \operatorname{CE}: \Alg_{\spLie}(\Sp)\xrightarrow{\Sigma'} \Alg_{\BL}(\Sp)
        \xrightarrow{\cot_{\BL}}
        \Sp
        $
        where $\Sigma'$ is the equivalence in Lemma \ref{Shift has no harm};
        \item $
        \widetilde{\operatorname{CE}}: \Alg_{\spLie}(\Sp)\xrightarrow{\Sigma'} \Alg_{\BL}(\Sp)
        \xrightarrow{\indec_{\BL}}
        \coAlg^{\divpow, \nil}_{\Com}(\Sp).
        $
    \end{itemize}
\end{definition}

For later application, we record the following theorem from \cite{Ching-Harper}.
\begin{theorem}
\cite{Ching-Harper}
\label{Ching-Harper's Koszul duality}
	Let $R$ be an $\E_{\infty}$-ring spectrum and $\CO$ an operad in the $\infty$-category $\Mod_R$ of $R$-module spectra with $\CO(1)=R$. Suppose $R$ and all $\CO(n)$ are connective. Then the functor 
	\[
	\indec_{\CO}: \Alg_{\CO}(\Mod_R)^{\geq 1} \to \coAlg^{nil, dp}_{\Barconstruction(\CO)}(\Mod_R)^{\geq 1}
	\]
	 is an equivalence.
\end{theorem}

Taking $R=H\BZ$ and let $\Lie$ denote the Lie operad in $\Mod_{H\BZ}$, we obtain the following corollary.
\begin{corollary}
	For $r\geq 1$, the Chevalley-Eilenberg functor 
	\[
	\widetilde{\operatorname{CE}}: \Alg_{\Lie}(\Mod_{H\BZ})^{\geq r} \to \coAlg^{nil, dp}_{\Com}(\Mod_{H\BZ})^{\geq r}
	\]
	is an equivalence of $\infty$-categories.
\end{corollary}

We now define the Chevalley-Eilenberg functor for tame spectral Lie algebras. First we need the following lemma regarding the bar construction of the monad $(L_{\tame})_{!}F_{\CO}$.
\begin{lemma}
    Let $\CO$ be a connected $\infty$-operad in $ \Sp$ and let $F_{\CO}$ be the induced monad on $\Sp^{\geq r}$,
    then 
    $$
    \Barconstruction(L_{\tame}F_\CO ) \simeq L_{\tame} \Barconstruction(F_\CO).
    $$
\end{lemma}
\begin{proof}
    Unravelling the definition of bar construction, we need to show there is an equivalence
    $$
     |\Barconstruction(\id, L_{\tame}\CO , \id)_{\bullet}|
     \simeq
     L_{\tame}|\Barconstruction(\id, \CO , \id)_{\bullet}|.
    $$
    Since $L_{\tame}$ preserves colimits, the proof is reduced to checking that
    there is a tame equivalence
    \begin{equation}
    \label{Eq. 3.6.17.}
    \Barconstruction(\id, \CO , \id)_{\bullet}
    \to 
    \Barconstruction(\id, L_{\tame}\CO , \id)_{\bullet}
    \end{equation}
    of simplicial objects in $\Monad(\Sp^{\geq r})$. 
    We claim that there is an equivalence
    $$
    L_{\tame} (\underbrace{\CO \circ \cdots \circ \CO}_{\text{$n$-fold}} )
    \simeq 
    \underbrace{ L_{\tame}\CO \circ \cdots \circ  L_{\tame}\CO}_{\text{$n$-fold}} 
    $$
    for each $n\geq 1$.
    It suffices to check this for two-fold composition, which can be done directly on the composition of the associated Schur functors
    $$
    F_{\CO}(X):= \coprod_{n\geq 1} (\CO(n) \otimes X^{\otimes n})_{h\Sigma_n}.
    $$ 
    The desired equivalence follows from the fact that $L_{\tame}$ is symmetric monoidal and preserves colimits.
    Therefore, the map (\ref{Eq. 3.6.17.}) is a point-wise tame equivalence, which is a tame equivalence after taking geometric realization.
\end{proof}

As a consequence, taking $\CO=\spLie$ allows us to identify the bar construction of the monad $L_{\tame}F_{\spLie}$ as the comonad $L_{\tame}F_{\Com}$. Explicitly, by Proposition \ref{Cofreee commutative comonad}, the underlying endofunctor of the comonad $L_{\tame}F_{\Com}$ on a tame spectrum $X$ is given by
$$
X \mapsto \coprod_{n\geq 1} L_{\tame} (X^{\otimes n})_{h\Sigma_n}.
$$
Therefore, we obtain a functor 
$$
L_{\tame} \indec_{\BL}:
\Alg_{\BL}(\Sp^{\geq r+1}_{\tame})
\to
\coAlg^{\divpow, \nil}_{\Com}(\Sp^{\geq r+1}_{\tame}).
$$

Note that there is an equivalence of $\infty$-categories between $r$-tame spectra and $(r+1)$-tame spectra by Lemma \ref{Relations between different tameness}, hence we obtain a pullback diagram 
\[
    \begin{tikzcd}
	\Alg_{\spLie}(\Sp^{\geq r}_{\tame})    & \Alg_{\BL}(\Sp^{\geq r+1}_{\tame})\\
	 \Sp^{\geq r}_{\tame} & \Sp^{\geq r+1}_{\tame}
	\arrow[from=1-1, to = 1-2, "\Sigma'", "\simeq" below]
	\arrow[from=1-1 , to =2-1,  left]
	\arrow[from=1-2 , to =2-2,  right]
	\arrow[from=2-1, to=2-2, "\Sigma", "\simeq" below]
\end{tikzcd}
\]
as in Lemma \ref{Shift has no harm}.

\begin{definition}
\label{Chevalley-Eilenberg functor for tame spectra}
We define the Chevalley-Eilenberg functor for tame spectra
to be the following composite
$$
\tildeCE_{\tame}: \Alg_{\spLie}(\Sp^{\geq r}_{\tame})
\xrightarrow[\simeq]{\Sigma'}
\Alg_{\BL}(\Sp^{\geq r+1}_{\tame})
\xrightarrow{L_{\tame} \indec_{\BL}}
\coAlg^{\divpow, \nil}_{\Com}(\Sp^{\geq r+1}_{\tame}).
$$
\end{definition}

\begin{definition}
The functor $\tildeCE_{\tame}$ admits a right adjoint by the adjoint functor theorem, which we will denote by $\widetilde{\Prim}$.
\end{definition}

% We end this section with a result concerning the Chevalley-Eilenberg functor on tame spectra of different degrees.
% \begin{proposition}
% $$

% $$
% \end{proposition}

\begin{remark}
\label{Formula for computing CE_tame(L)}
The underlying spectrum of $\tildeCE_{\tame}(L)$ can be computed as the geometric realization of the bar construction 
$$
|B(\id_{\Sp^{\geq r+1}_{\tame}}, L_{\tame}F_{\BL}\circ \Sigma', \id_{\Sp^{\geq r+1}_{\tame}})|
$$
which is equivalent to $L_{\tame}\tildeCE(L)$ as $L_{\tame}$ is colimit-preserving and symmetric monoidal.
\end{remark}

\begin{lemma}
\label{Lemma 3.6.20}
There are equivalences of functors
$$
\tildeCE_{\tame}\circ \trivial_{\spLie}\simeq \Sym_{\tame}\circ \Sigma
$$
and
$$
\widetilde{\Prim}\circ \Sym_{\tame} \simeq \trivial_{\spLie}\circ \Omega.
$$
\end{lemma}
\begin{proof}
    The proof is analogous to that of Lemma \ref{CE of Trivial is cofree}, plus the equivalences 
    $
    \trivial_{\BL}\circ \Sigma \simeq \Sigma'\circ \trivial_{\spLie} 
    $
    and $\Omega' \circ \trivial_{\BL} \simeq \trivial_{\spLie}\circ \Omega $.
    
\end{proof}



% Consider the functor $\trivial_{\spLie}:\Sp^{\geq r}_{\tame}\to \Alg_{\spLie}(\Sp^{\geq r}_{\tame})$ and $$
% \indec_{\BL}:\Alg_{\BL}(\Sp^{\geq r+1}_{\tame})
% \to
% \coAlg^{\divpow, \nil}_{\Com}(\Sp^{\geq r+1}_{\tame}).
% $$



Proposition \ref{all coalgebras are equivalent} allows us to identify the codomain of the Chevalley-Eilenberg functor $\tildeCE_{\tame}$ on tame spectra as $\coCAlg(\Sp^{\geq r}_{\tame})$, whose categorical product is given by the tensor product $\hat{\otimes}$ in $\Sp^{\geq}_{\tame}$.
We now show that the Chevalley-Eilenberg functor $\widetilde{\operatorname{CE}}$ preserves finite products, hence it induces a functor on the categories of group objects.
\begin{lemma}
\label{CE preserves products}
	The functor 
	$\widetilde{\operatorname{CE}}_{\tame}$
	preserves finite products.
\end{lemma}
\begin{proof}
    Since $\Sigma'$ is an equivalence, it suffices to show
	the natural morphism 
	\[
	L_{\tame}\indec_{\BL}(L \times L') 
	\to 
	L_{\tame}\indec_{\BL}(L)\hat{\otimes} 
	L_{\tame}\indec_{\BL}(L') 
	\]
	is an equivalence for $L,L' \in \Alg_{\BL}(\Sp^{\geq r}_{\tame}$). 
	By Remark \ref{Formula for computing CE_tame(L)}, the proof reduces to showing that the natural map 
	\[
    c:	\indec_{\BL}(L \times L') 
	\to 
	\indec_{\BL}(L)\otimes \indec_{\BL}(L') 
	\]
	is a tame equivalence when we regard $L,L'$ as objects in $\Alg_{\BL}(\Sp)$.

	For a spectral Lie algebra $X$, we let $X_*$ denote its canonical filtration from Theorem \ref{Canonical grading on an O-algebra}. 
	Note that $\indec_{\BL}$ induces a functor 
	$$
	(\indec)_*: \Fil^{+}(\Alg_{\BL}(\Sp))
	\to 
	\Fil^{+}(\coCAlg^{\divpow,\nil}(\Sp))
	$$
	by postcomposing with $\indec_{\BL}$.
	Since $X\simeq \colim X_*$ and $\indec_{\BL}$ preserves colimits, it suffices to show $c$ induces an equivalence on the canonical filtrations, i.e.,
	$$
	(\indec_{\BL})_*(L_* \times L'_*)
	\to 
	(\indec_{\BL})_*(L_*) \otimes (\indec_{\BL})_*(L'_*).
	$$
	Note also that the associated graded functor $\Graded$ is conservative by Lemma \ref{Ass-gr is conservative}, hence the proof further reduces to proving that the induced map on associated gradeds
    \[
    \nu:
	\Graded (\indec_{\BL})_*( (L \times L')_{*} )
	\to 
	\Graded ((\indec_{\BL})_*(L_*)\otimes (\indec_{\BL})_*(L'_*))
	\]
	is an equivalence.
	
	Since $\Graded$ is symmetric monoidal by Remark \ref{BM def 2.5}, and it commutes with $(\indec_{\BL})_*$ (since $\Graded$ is defined using colimits), there are equivalences
	$$
	\Graded (\indec_{\BL})_*( (L \times L')_{*} )
	\simeq \indec_{\BL}^{\Graded} (\Graded (L\times L')_{*})
	$$
	and 
	$$
	\Graded ((\indec_{\BL})_*(L_*)\otimes (\indec_{\BL})_*(L'_*)) 
	\simeq 
	\indec^{\Graded}_{\BL}(\Graded(L_*)) \otimes 
	\indec^{\Graded}_{\BL}(\Graded(L'_*))
	$$
	where $\indec^{\Graded}_{\BL}$ denotes the induced functor on associated graded. Hence we can identify $\nu$ as the map
	$$
	\indec_{\BL}^{\Graded} (\Graded (L\times L')_{*}) 
	\to 
	\indec^{\Graded}_{\BL}(\Graded(L_*)) \otimes 
	\indec^{\Graded}_{\BL}(\Graded(L'_*)).
	$$
	
	By theorem \ref{Canonical grading on an O-algebra}, the associated graded of the canonical filtration of a spectral Lie algebra $X$ has the form 
	$$
	\Free_{\BL}((B\BL(n)\otimes X^{\otimes n})_{h\Sigma_n} \simeq \Free_{\BL}(X^{\otimes n})_{h\Sigma_n}
	$$
	where the latter equivalence comes from the fact that $B\BL\simeq \Com$. 
	Hence, there are equivalences
	\begin{align*}
	\oblv_{\BL}\indec_{\BL}
	\Free_{\BL}(X^{\otimes n})_{h\Sigma_n}
	&\simeq 
	\cot_{\BL}\circ \Free_{\BL}(X^{\otimes n})_{h\Sigma_n}  \\	    
	&\simeq (X^{\otimes n})_{h\Sigma_n} \\
	& = \Sym^n(X).
	\end{align*}

	Therefore, the map $\oblv(\nu)$ is equivalent to the natural map
	$$
	\Sym (L\times L') \to \Sym(L) \otimes \Sym(L'),
	$$
	which is a tame equivalence since the symmetric coalgebra functor $\Sym$ is the cofree coalgebra comonad which preserves products and the tensor product in $\Sp^{\geq r}_{\tame}$ is the product in $\coCAlg^{\divpow,\nil}(\Sp^{\geq r}_{\tame})\simeq \coCAlg(\Sp^{\geq r}_{\tame})$.

\end{proof}













